---
title: '[8B]_Echolocation_Insect-eating-bats'
author: "Paula Iturralde"
date: '2025-02-04'
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}


# required packages
library(lme4)
library(lsmeans)
library(tidyverse)
library(ggpubr)
library(pbapply)
library(effects)
library(ggeffects)
library(ggExtra)
library(ggfortify)
library(sjPlot)
library(gridExtra)
library(lsmeans)
library(jtools)
library(effectsize)
library(plotly)
library(viridis)
library(plot3D)
library(lme4)
library(segmented)

```

```{r}

Data_GLM30 <- read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_codes/AAA/DataWdist/AADD_30Wdist_thr1.csv", header = T, sep = ";")
Data_GLM30 <- as.data.frame(Data_GLM30[,-1])
colnames(Data_GLM30)
str(Data_GLM30)


Ind = as.data.frame(sprintf("%03d", Data_GLM30$Ind))
names(Ind)[1]<-paste("Ind")
Data_GLM30 <- cbind(Data_GLM30, Ind)
Data_GLM30 <- Data_GLM30[, c(1:2,74,4:73)]
Data_GLM30[, 'Ind'] <- as.factor(Data_GLM30[,'Ind'])

i <- c(37:39)#create the i vector with the columns that I need to be numeric
Data_GLM30[ , i] <- apply(Data_GLM30[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10,11,73)#create the i vector with the columns that I need to be as.character

Data_GLM30[ , i] <- apply(Data_GLM30[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))



#make Date_Time column as.Date

Data_GLM30$Date_Time <- gsub('_', ' ', Data_GLM30$Date_Time) #deparate date and time by space
Data_GLM30$Date <- sapply(strsplit(as.character(Data_GLM30$Date_Time), " "), "[", 1) #make date 1 column
Data_GLM30$Time <- sapply(strsplit(as.character(Data_GLM30$Date_Time), " "), "[", 2) #make time 2 column
Data_GLM30$Time <- gsub('-', ':', Data_GLM30$Time) #change - for : for correct time format 
Data_GLM30$Date_Time <- as.POSIXct(paste(Data_GLM30$Date, Data_GLM30$Time), format="%Y-%m-%d %H:%M:%S") #make as.Date
Data_GLM30 <- Data_GLM30[,-c(74,75)] #delete columns of date and time that we don't need anymore. 

str(Data_GLM30)
nrow(Data_GLM30)
colnames(Data_GLM30)
head(Data_GLM30)

names(Data_GLM30)[names(Data_GLM30) == 'T'] <- 'temp'
colnames(Data_GLM30)
#View(Data_GLM30)

```

# Check Harmonic 

```{r}

#Check harmonic

Data_GLM30$Harmonic = case_when(
        Data_GLM30$Species=="M.oxyotus" & Data_GLM30$PF_E12 <=70 ~ "1st",
        Data_GLM30$Species=="M.keaysi" & Data_GLM30$PF_E12 <=85 ~ "1st", 
        Data_GLM30$Species=="M.riparius" & Data_GLM30$PF_E12 <=85 ~ "1st",
        Data_GLM30$Species=="M.albescens" & Data_GLM30$PF_E12 <=85 ~ "1st",
        Data_GLM30$Species=="M.elegans" & Data_GLM30$PF_E12 <=85 ~ "1st",
        Data_GLM30$Species=="M.nigricans" & Data_GLM30$PF_E12 <=80 ~ "1st",
        Data_GLM30$Species=="E.brasiliensis" & Data_GLM30$PF_E12 <=75 ~ "1st")

#Replace the NA's that does not belong to the previous condition with "2nd" (second harmonic)        
Data_GLM30$Harmonic [is.na(Data_GLM30$Harmonic )] <- "2nd"
Data_GLM30$Harmonic

Data_GLM30<- subset(Data_GLM30, Harmonic != "2nd") 
nrow(Data_GLM30)
colnames(Data_GLM30)
Data_GLM30$Session

Data_GLM30 <- Data_GLM30[!is.na(Data_GLM30$distB2Mic),]
nrow(Data_GLM30)
colnames(Data_GLM30)

#View(Data_GLM30[, c("GS", "Ind","Rec","TRJ","Exp","distB2Mic","dur_E12","Mean_dur_E12")])

Data_GLM30 <- Data_GLM30 %>% 
  mutate(dist_cat = ifelse(distB2Mic < 1.5, "<1.5", ">1.5"))

length(which(Data_GLM30$dist_cat == "<1.5"))
length(which(Data_GLM30$dist_cat == ">1.5"))

```

# Make a Summary table for parameters

```{r}

# Make a summary table for all parameters per individual 

colnames(Data_GLM30)
var_sumary <- Data_GLM30 %>%
  group_by(GS,Ind,Exp) %>%
  summarise(
    minRH = min(RH),
    maxRH = max(RH),
    meanRH = mean(RH),
    minT = min(temp),
    maxT = max(temp),
    meanT = mean(temp),
    minPF = min(PF_E12),
    maxPF = max(PF_E12),
    meanPF = mean(PF_E12),
    sdPF = sd(PF_E12),
    minSL = min(rmsSL_E12_10cm),
    maxSL = max(rmsSL_E12_10cm),
    meanSL = mean(rmsSL_E12_10cm),
    sdSL = sd(rmsSL_E12_10cm),
    minDur = min(dur_E12),
    maxDur = max(dur_E12),
    meanDur = mean(dur_E12),
    sdDur = sd(dur_E12),
    minAA = max(AAFp),
    maxAA = min(AAFp),
    meanDD = mean(AAFp),
    sdAA = sd(AAFp),
    minDD = min(realDD2),
    maxDD = max(realDD2),
    meanDD = mean(realDD2),
    sdDD = sd(realDD2),
  )
#Replace the NA's with 0        
var_sumary$sdPF [is.na(var_sumary$sdPF)] <- 0
var_sumary$sdSL [is.na(var_sumary$sdSL)] <- 0
var_sumary$sdDur [is.na(var_sumary$sdDur)] <- 0
var_sumary$sdAA [is.na(var_sumary$sdAA)] <- 0
var_sumary$sdDD [is.na(var_sumary$sdDD)] <- 0


dotCOLS = c("dodgerblue2","darkgoldenrod1","cyan4","darkolivegreen4","coral3")
barCOLS = c("dodgerblue2","darkgoldenrod1","cyan4","darkgolivegreen4","coral3")


RecNum   <- aggregate(Data_GLM30[,c(4)], by=Data_GLM30[,c(2,3,6,8)], length)
#write.csv(RecNum, file = "F:/PhD_Project/Sensory_Ecology/R/R_codes/AAA/DataWdist/Rec_num.csv", row.names = FALSE)

RecNum <- read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_codes/AAA/DataWdist/Rec_num_ed.csv", header = T, sep = ";")


```


#Plot Peak Frequency individual variation per experiment

```{r}

PFvar <- ggplot(var_sumary, aes(x=GS, group=Ind, y=meanPF, ymin=meanPF-sdPF, ymax=meanPF+sdPF, color=GS)) + 
  #specify position here
    geom_linerange(size=0.1,position=position_dodge(width = 1),show.legend = FALSE) +
  #  geom_hline(yintercept=60, lty=2) +
  #specify position here too
    geom_point(size=2, shape=20, stroke = 0.1,position=position_dodge(width = 1),show.legend = FALSE) +
    geom_vline(xintercept = c(1.52, 2.48,3.52,4.52), linetype = "solid") +
    scale_fill_manual(values=barCOLS)+
    scale_color_manual(values=dotCOLS)+
    scale_x_discrete(name="Bat Species") +
    facet_wrap(~Exp)+
    scale_y_continuous(name="Peak Frequency (kHz)", limits = c(35, 90)) +
    coord_flip() +
    theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=12),
                     axis.title.y=element_blank(),
                     axis.text.y=element_blank(),
                     axis.ticks.y=element_blank())

PFvar

```

#Plot Soure Level individual variation per experiment 

```{r}

#Plot Source Level 
SLvar <- ggplot(var_sumary, aes(x=GS, group=Ind, y=meanSL, ymin=meanSL-sdSL, ymax=meanSL+sdSL, color=GS)) + 
  #specify position here
    geom_linerange(size=0.1,position=position_dodge(width = 1),show.legend = FALSE) +
  #  geom_hline(yintercept=60, lty=2) +
  #specify position here too
    geom_point(size=2, shape=20, stroke = 0.1,position=position_dodge(width = 1),show.legend = FALSE) +
    geom_vline(xintercept = c(1.52, 2.48,3.52,4.52), linetype = "solid") +
    scale_fill_manual(values=barCOLS)+
    scale_color_manual(values=dotCOLS)+
    scale_x_discrete(name="Bat Species") +
    facet_wrap(~Exp)+
    scale_y_continuous(name="apSource Level (dB @ 10cm re 20µPa)", limits = c(95, 125)) +
    coord_flip() +
    theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=12),
                     axis.title.y=element_blank(),
                     axis.text.y=element_blank(),
                     axis.ticks.y=element_blank())

SLvar

```


#Plot Duration individual variation per experiment

```{r}

Durvar<-ggplot(var_sumary, aes(x=GS, group=Ind, y=meanDur, ymin=meanDur-sdDur, ymax=meanDur+sdDur, color=GS)) + 
  #specify position here
    geom_linerange(size=0.1,position=position_dodge(width = 1),show.legend = FALSE) +
  #  geom_hline(yintercept=60, lty=2) +
  #specify position here too
    geom_point(size=2, shape=20, stroke = 0.1,position=position_dodge(width = 1),show.legend = FALSE) +
    geom_vline(xintercept = c(1.52, 2.48,3.52,4.52), linetype = "solid") +
    scale_fill_manual(values=barCOLS)+
    scale_color_manual(values=dotCOLS)+
    scale_x_discrete(name="Bat Species") +
    facet_wrap(~Exp)+
    scale_y_continuous(name="Duration (ms)", limits = c(0.5, 3)) +
    coord_flip() +
    theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=12),
                     axis.title.y=element_blank(),
                     axis.text.y=element_blank(),
                     axis.ticks.y=element_blank())

Durvar

```

#Summarize data per species


```{r}
str(Data_GLM30)
#View(GS_summary)
GS_summary <- Data_GLM30 %>%
  group_by(GS,Exp) %>%
  summarise(
    minPF = min(PF_E12),
    maxPF = max(PF_E12),
    meanPF = mean(PF_E12),
    sdPF = sd(PF_E12),
    minSL = min(rmsSL_E12_10cm),
    maxSL = max(rmsSL_E12_10cm),
    meanSL = mean(rmsSL_E12_10cm),
    sdSL = sd(rmsSL_E12_10cm),
    minDur = min(dur_E12),
    sdPF = sd(PF_E12),
    maxDur = max(dur_E12),
    meanDur = mean(dur_E12),
    sdDur = sd(dur_E12),
    minAA = max(AAFp),
    maxAA = min(AAFp),
    meanDD = mean(AAFp),
    sdAA = sd(AAFp),
    minDD = min(realDD2),
    maxDD = max(realDD2),
    meanDD = mean(realDD2),
    sdDD = sd(realDD2),
  )


#Replace the NA's with 0        
GS_summary$sdPF [is.na(GS_summary$sdPF)] <- 0
GS_summary$sdSL [is.na(GS_summary$sdSL)] <- 0
GS_summary$sdDur [is.na(GS_summary$sdDur)] <- 0
GS_summary$sdAA [is.na(GS_summary$sdAA)] <- 0
GS_summary$sdDD [is.na(GS_summary$sdDD)] <- 0

# This is to calculate the mean RH per experiment
RH_temp_mean <- Data_GLM30 %>%
  group_by(Exp) %>%
  summarise(
    mean_temp = mean(temp, na.rm = TRUE),
    mean_RH = mean(RH, na.rm = TRUE)
  )

```

# Separate dataset by species

```{r}
#Separate dataset by group of species
colnames(Data_GLM30)
GLM_Mo30 <- Data_GLM30[ which(Data_GLM30$GS=="M.oxyotus"),]
GLM_Mk30 <- Data_GLM30[ which(Data_GLM30$GS=="M.keaysi"),]
GLM_Mr30 <- Data_GLM30[ which(Data_GLM30$GS=="M.riparius"),]
GLM_Mg30 <- Data_GLM30[ which(Data_GLM30$GS=="M.group"),]
GLM_Eb30 <- Data_GLM30[ which(Data_GLM30$GS=="E.brasiliensis"),]


```

#Models 
#Myotis oxyotus
#Peak Frequency

```{r}

Mo_mPF_nd <- lmer(PF_E12 ~ temp + (temp|Ind), data=GLM_Mo30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope no distance
Mo_mPF_wd <- lmer(PF_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mo30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope with distance

#Mixed models summary
coef(Mo_mPF_nd)
summary(Mo_mPF_nd)
anova(Mo_mPF_nd)
Mo_tPF_nd <- sjPlot:: tab_model(Mo_mPF_nd)
#Random slope models summary
coef(Mo_mPF_wd)
summary(Mo_mPF_wd)
anova(Mo_mPF_wd)
  #Random slope models summary

tab_model(Mo_mPF_nd, Mo_mPF_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMoPF_nd <- effect("temp", Mo_mPF_nd)
efMoPF_nd <- as.data.frame(efMoPF_nd)
efMoPF_nd

efMoPF_wd <- effect("temp", Mo_mPF_wd)
efMoPF_wd <- as.data.frame(efMoPF_wd)
efMoPF_wd

#Effect sizes
effectsize(Mo_mPF_nd)
effectsize(Mo_mPF_wd)

#create table with confidence intervals
ggpredict(Mo_mPF_nd, "temp")
ggpredict(Mo_mPF_nd, "temp")

```

#Plots 
#Myotis oxyotus
#Peak Frequency

```{r}

# Extract fixed effects coefficients from the model
fe_Mo_mPF_wd <- fixef(Mo_mPF_wd)

# Create a function to calculate predicted values using model coefficients
calculate_predicted <- function(temp, distB2Mic) {
  predicted <- fe_Mo_mPF_wd["(Intercept)"] +
               fe_Mo_mPF_wd["temp"] * temp +
               fe_Mo_mPF_wd["distB2Mic"] * distB2Mic +
               fe_Mo_mPF_wd["temp:distB2Mic"] * temp * distB2Mic
  return(predicted)
}

# Extract predicted values from the model
pred_Mo_mPF_wd <- predict(Mo_mPF_wd, newdata = GLM_Mo30, re.form = NA)
# Generate predicted values for each combination of temperature and distance to microphone
tr_Mo_mPF_wd <- seq(min(GLM_Mo30$temp), max(GLM_Mo30$temp), length.out = 30)
dr_Mo_mPF_wd <- seq(min(GLM_Mo30$distB2Mic), max(GLM_Mo30$distB2Mic), length.out = 30)
pred_Mo_mPF_wd <- matrix(NA, nrow = length(tr_Mo_mPF_wd), ncol = length(dr_Mo_mPF_wd))

for (i in 1:length(tr_Mo_mPF_wd)) {
  for (j in 1:length(dr_Mo_mPF_wd)) {
    pred_Mo_mPF_wd[i, j] <- calculate_predicted(tr_Mo_mPF_wd[i], dr_Mo_mPF_wd[j])
  }
}

# Create data frame for plotting
gr_Mo_mPF_wd <- expand.grid(temp = tr_Mo_mPF4, distB2Mic = dr_Mo_mPF4)
gr_Mo_mPF_wd$pred_PF <- as.vector(pred_Mo_mPF4)

#OPTION 2
# Plot image with discrete colors
p2Mo_mPF_wd <- ggplot(gr_Mo_mPF_wd, aes(x = temp, y = distB2Mic, fill = cut(pred_PF, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "Predicted PF") +
  scale_fill_manual(values = colors) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold")  # Increase y-axis title size
  )

# Definir la ruta y el nombre del archivo
Mo_PF <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/p2Mo_mPF4.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mo_PF, plot = p2Mo_mPF4, dpi = 300, width = 15, height = 10, units = "cm")


# Create a grid of values for temp and distB2Mic
tr2_Mo_mPF_wd <- GLM_Mo30$temp #temperature
dr2_Mo_mPF_wd <- GLM_Mo30$distB2Mic #distance
ind2_Mo_mPF_wd <- GLM_Mo30$Ind #individual
pred2_Mo_mPF_wd <- predict(Mo_mPF_wd) #predictors

# Crear un dataframe
df_Mo_mPF_wd <- data.frame(
              temp = tr2_Mo_mPF_wd,
              dist = dr2_Mo_mPF_wd,
              ind = ind2_Mo_mPF_wd,
              pred = pred2_Mo_mPF_wd
)

head(GLM_Mo30)

```

#Models 
#Myotis oxyotus
#Source Level

```{r}

#Source Level
Mo_mSL_nd <- lmer(rmsSL_E12_10cm ~ temp + (temp|Ind), data=GLM_Mo30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope no distance
Mo_mSL_wd <- lmer(rmsSL_E12_10cm ~ temp * distB2Mic + (temp|Ind), data=GLM_Mo30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope with distance


#Mixed models summary
coef(Mo_mSL_nd)
summary(Mo_mSL_nd)
anova(Mo_mSL_nd)
Mo_tPF_nd <- sjPlot:: tab_model(Mo_mSL_nd)
#Random slope models summary
coef(Mo_mSL_wd)
summary(Mo_mSL_wd)
anova(Mo_mSL_wd)
  #Random slope models summary

tab_model(Mo_mSL_nd, Mo_mSL_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMoSL_nd <- effect("temp", Mo_mSL_nd)
efMoSL_nd <- as.data.frame(efMoSL_nd)
efMoSL_nd

efMoSL_wd <- effect("temp", Mo_mSL_wd)
efMoSL_wd <- as.data.frame(efMoSL_wd)
efMoSL_wd

#Effect sizes
effectsize(Mo_mPF_nd)
effectsize(Mo_mPF_wd)

#create table with confidence intervals
ggpredict(Mo_mSL_nd, "temp")
ggpredict(Mo_mSL_wd, "temp")


```

#Plots 
#Myotis oxyotus
#Source Level

```{r}

#Original plots
#M. oxyotus
pMoSL_wd <- ggplot() + 
#geom_point(data=efMoSLm_wd, aes(temp,fit)) + 
  geom_line(data=efMoSLm_wd, aes(x=temp, y=fit), color="darkolivegreen4", size=3) +
  #geom_point(data=efMoSLm_wd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efMoSLm_wd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)",y="apSL (dB@10cm_re20µPa)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMoSL <- pMoSL + geom_point(data=GLM_Mo30, aes(temp,rmsSL_E12_10cm), size=1.5, colour="darkolivegreen4" ) + xlim(18, 25) + theme(axis.text.x=element_text(size=15))

# Definir la ruta y el nombre del archivo
Mo_SL <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMoSL.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mo_SL, plot = pMoSL, dpi = 300, width = 15, height = 10, units = "cm")

```

#Models 
#Myotis oxyotus
#Duration

```{r}

#Duration
Mo_mDur_nd <- lmer(dur_E12 ~ temp + (temp|Ind), data=GLM_Mo30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope no distance
Mo_mDur_wd <- lmer(dur_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mo30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope with distance

#Mixed models summary
coef(Mo_mDur_nd)
summary(Mo_mDur_nd)
anova(Mo_mDur_nd)
Mo_tPF_nd <- sjPlot:: tab_model(Mo_mDur_nd)
#Random slope models summary
coef(Mo_mDur_wd)
summary(Mo_mDur_wd)
anova(Mo_mDur_wd)
  #Random slope models summary

tab_model(Mo_mDur_nd, Mo_mDur_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMoDur_nd <- effect("temp", Mo_mDur_nd)
efMoDur_nd <- as.data.frame(efMoDur_nd)
efMoDur_nd

efMoDur_wd <- effect("temp", Mo_mDur_wd)
efMoDur_wd <- as.data.frame(efMoDur_wd)
efMoDur_wd

#Effect sizes
effectsize(Mo_mPF_nd)
effectsize(Mo_mPF_wd)

#create table with confidence intervals
ggpredict(Mo_mDur_nd, "temp")
ggpredict(Mo_mDur_wd, "temp")

```

#Plots 
#Myotis oxyotus
#Duration

```{r}

#Original plots
#M. oxyotus
pMoDur_wd <- ggplot() + 
#geom_point(data=efMoDur_wd, aes(temp,fit)) + 
  geom_line(data=efMoDur_wd, aes(x=temp, y=fit), color="darkolivegreen4", size=3) +
  #geom_point(data=efMoDur_wd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efMoDur_wd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)",y="Duration (ms)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMoDur <- pMoDur + geom_point(data=GLM_Mo30, aes(temp,dur_E12), size=1.5, colour="darkolivegreen4") + 
  xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
Mo_Dur <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMoDur.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mo_Dur, plot = pMoDur, dpi = 300, width = 15, height = 10, units = "cm")

```

#Models 
#Myotis pilosatibialis
#Peak Frequency

```{r}

Mk_mPF_nd <- lmer(PF_E12 ~ temp + (temp|Ind), data=GLM_Mk30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope no distance
Mk_mPF_wd <- lmer(PF_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mk30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope with distance

#Mixed models summary
coef(Mk_mPF_nd)
summary(Mk_mPF_nd)
anova(Mk_mPF_nd)
Mk_tPF_nd <- sjPlot:: tab_Model(Mk_mPF_nd)
#Random slope models summary
coef(Mk_mPF_wd)
summary(Mk_mPF_wd)
anova(Mk_mPF_wd)
  #Random slope models summary

tab_model(Mk_mPF_nd, Mk_mPF_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMkPF_nd <- effect("temp", Mk_mPF_nd)
efMkPF_nd <- as.data.frame(efMkPF_nd)
efMkPF_nd

efMkPF_wd <- effect("temp", Mk_mPF_wd)
efMkPF_wd <- as.data.frame(efMkPF_wd)
efMkPF_wd

#Effect sizes
effectsize(Mk_mPF_nd)
effectsize(Mk_mPF_wd)

#create table with confidence intervals
ggpredict(Mk_mPF_nd, "temp")
ggpredict(Mk_mPF_nd, "temp")

```

#Plots 
#Myotis pilosatibialis
#Peak Frequency

```{r}

# Extract fixed effects coefficients from the model
fe_Mk_mPF_wd <- fixef(Mk_mPF_wd)

# Create a function to calculate predicted values using model coefficients
calculate_predicted <- function(temp, distB2Mic) {
  predicted <- fe_Mk_mPF_wd["(Intercept)"] +
               fe_Mk_mPF_wd["temp"] * temp +
               fe_Mk_mPF_wd["distB2Mic"] * distB2Mic +
               fe_Mk_mPF_wd["temp:distB2Mic"] * temp * distB2Mic
  return(predicted)
}

# Extract predicted values from the model
pred_Mk_mPF_wd <- predict(Mk_mPF_wd, newdata = GLM_Mo30, re.form = NA)
# Generate predicted values for each combination of temperature and distance to microphone
tr_Mk_mPF_wd <- seq(min(GLM_Mk30$temp), max(GLM_Mk30$temp), length.out = 30)
dr_Mk_mPF_wd <- seq(min(GLM_Mk30$distB2Mic), max(GLM_Mk30$distB2Mic), length.out = 30)
pred_Mk_mPF_wd <- matrix(NA, nrow = length(tr_Mk_mPF_wd), ncol = length(dr_Mk_mPF_wd))

for (i in 1:length(tr_Mk_mPF_wd)) {
  for (j in 1:length(dr_Mk_mPF_wd)) {
    pred_Mk_mPF_wd[i, j] <- calculate_predicted(tr_Mk_mPF_wd[i], dr_Mk_mPF_wd[j])
  }
}

# Create data frame for plotting
gr_Mk_mPF_wd <- expand.grid(temp = tr_Mk_mPF4, distB2Mic = dr_Mk_mPF4)
gr_Mk_mPF_wd$pred_PF <- as.vector(pred_Mk_mPF4)


#OPTION 2
# Plot image with discrete colors
p2Mk_mPF_wd <- ggplot(gr_Mk_mPF4, aes(x = temp, y = distB2Mic, fill = cut(pred_PF, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "Predicted PF") +
  scale_fill_manual(values = colors) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold")  # Increase y-axis title size
  )

# Definir la ruta y el nombre del archivo
Mk_PF <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/p2Mk_mPF4.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mk_PF, plot = p2Mk_mPF4, dpi = 300, width = 15, height = 10, units = "cm")

```

#Models 
#Myotis pilosatibialis
#Source Level

```{r}

#Source Level
Mk_mSL_nd <- lmer(rmsSL_E12_10cm ~ temp + (temp|Ind), data=GLM_Mk30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope no distance
Mk_mSL_wd <- lmer(rmsSL_E12_10cm ~ temp * distB2Mic + (temp|Ind), data=GLM_Mk30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope with distance


#Mixed models summary
coef(Mk_mSL_nd)
summary(Mk_mSL_nd)
anova(Mk_mSL_nd)
Mk_tPF_nd <- sjPlot:: tab_model(Mk_mSL_nd)
#Random slope models summary
coef(Mk_mSL_wd)
summary(Mk_mSL_wd)
anova(Mk_mSL_wd)
  #Random slope models summary

tab_model(Mk_mSL_nd, Mk_mSL_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMkSL_nd <- effect("temp", Mk_mSL_nd)
efMkSL_nd <- as.data.frame(efMkSL_nd)
efMkSL_nd

efMkSL_wd <- effect("temp", Mk_mSL_wd)
efMkSL_wd <- as.data.frame(efMkSL_wd)
efMkSL_wd

#Effect sizes
effectsize(Mk_mPF_nd)
effectsize(Mk_mPF_wd)

#create table with confidence intervals
ggpredict(Mk_mSL_nd, "temp")
ggpredict(Mk_mSL_wd, "temp")

```

#Plots
#Myotis pilosatibialis
#Source Level

```{r}

# Extract fixed effects coefficients from the model
fe_Mk_mSL_wd <- fixef(Mk_mSL_wd)

# Create a function to calculate predicted values using model coefficients
calculate_predicted <- function(temp, distB2Mic) {
  predicted <- fe_Mk_mSL_wd["(Intercept)"] +
               fe_Mk_mSL_wd["temp"] * temp +
               fe_Mk_mSL_wd["distB2Mic"] * distB2Mic +
               fe_Mk_mSL_wd["temp:distB2Mic"] * temp * distB2Mic
  return(predicted)
}


# Extract predicted values from the model
predict_Mk_mSL_wd <- predict(Mk_mSL_wd, newdata = GLM_Mk30, re.form = NA)
# Generate predicted values for each combination of temperature and distance to microphone
tr_Mk_mSL_wd <- seq(min(GLM_Mk30$temp), max(GLM_Mk30$temp), length.out = 30)
dr_Mk_mSL_wd <- seq(min(GLM_Mk30$distB2Mic), max(GLM_Mk30$distB2Mic), length.out = 30)
pred_Mk_mSL_wd <- matrix(NA, nrow = length(tr_Mk_mSL_wd), ncol = length(dr_Mk_mSL_wd))

for (i in 1:length(tr_Mk_mSL_wd)) {
  for (j in 1:length(dr_Mk_mSL_wd)) {
    pred_Mk_mSL_wd[i, j] <- calculate_predicted(tr_Mk_mSL_wd[i], dr_Mk_mSL_wd[j])
  }
}

# Create data frame for plotting
gr_Mk_mSL_wd <- expand.grid(temp = tr_Mk_mSL_wd, distB2Mic = dr_Mk_mSL_wd)
gr_Mk_mSL_wd$pred_SL <- as.vector(pred_Mk_mSL_wd)

#OPTION 2
# Plot image with discrete colors
p2Mk_mSL_wd <- ggplot(gr_Mk_mSL_wd, aes(x = temp, y = distB2Mic, fill = cut(pred_SL, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "Predicted SL") +
  scale_fill_manual(values = colors) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold")  # Increase y-axis title size
  )

# Definir la ruta y el nombre del archivo
Mk_SL <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/p2Mk_mSL4.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mk_SL, plot = p2Mk_mSL4, dpi = 300, width = 15, height = 10, units = "cm")


```

#Models 
#Myotis pilosatibialis
#Duration

```{r}

#Duration
Mk_mDur_nd <- lmer(dur_E12 ~ temp + (temp|Ind), data=GLM_Mk30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope no distance
Mk_mDur_wd <- lmer(dur_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mk30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope with distance

#Mixed models summary
coef(Mk_mDur_nd)
summary(Mk_mDur_nd)
anova(Mk_mDur_nd)
Mk_tPF_nd <- sjPlot:: tab_model(Mk_mDur_nd)
#Random slope models summary
coef(Mk_mDur_wd)
summary(Mk_mDur_wd)
anova(Mk_mDur_wd)
  #Random slope models summary

tab_model(Mk_mDur_nd, Mk_mDur_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMkDur_nd <- effect("temp", Mk_mDur_nd)
efMkDur_nd <- as.data.frame(efMkDur_nd)
efMkDur_nd

efMkDur_wd <- effect("temp", Mk_mDur_wd)
efMkDur_wd <- as.data.frame(efMkDur_wd)
efMkDur_wd

#Effect sizes
effectsize(Mk_mPF_nd)
effectsize(Mk_mPF_wd)

#create table with confidence intervals
ggpredict(Mk_mDur_nd, "temp")
ggpredict(Mk_mDur_wd, "temp")

```

#Plots 
#Myotis pilosatibialis
#Duration

```{r}

#Original plots
#M. pilosatibialis (Mk)
pMkDur <- ggplot() + 
#geom_point(data=efMkDur_nd, aes(temp,fit)) + 
  geom_line(data=efMkDur_nd, aes(x=temp, y=fit), color="cyan4", size=3) +
  #geom_point(data=efMkDur_nd, aes(x=temp, y=fit),color="black", size=2) +
  geom_ribbon(data=efMkDur_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)",y="Duration (ms)")+
  theme_bw() + theme(axis.title=element_text(size=15,face="bold"),
                     axis.text=element_text(size=15))

pMkDur <- pMkDur + geom_point(data=GLM_Mk30, aes(temp,dur_E12), size=1.5, colour="cyan4") + 
  xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
Mk_Dur <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMkDur.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mk_Dur, plot = pMkDur, dpi = 300, width = 15, height = 10, units = "cm")

```


#Models 
#Myotis riparius
#Peak Frequency

```{r}

Mr_mPF_nd <- lmer(PF_E12 ~ temp + (temp|Ind), data=GLM_Mr30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope
Mr_mPF_wd <- lmer(PF_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mr30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope


#Random slope models summary
coef(Mr_mPF_nd)
summary(Mr_mPF_nd)
anova(Mr_mPF_nd)
Mr_tPF_nd <- sjPlot:: tab_Model(Mr_mPF_nd)

#Random slope models summary
coef(Mr_mPF_wd)
summary(Mr_mPF_wd)
anova(Mr_mPF_wd)
Mr_tPF_wd <- sjPlot:: tab_model(Mr_mPF_wd)


tab_model(Mr_mPF_nd, Mr_mPF_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMrPF_nd <- effect("temp", Mr_mPF_nd)
efMrPF_nd <- as.data.frame(efMrPF_nd)
efMrPF_nd

efMrPF_wd <- effect("temp", Mr_mPF_wd)
efMrPF_wd <- as.data.frame(efMrPF_wd)
efMrPF_wd

#Effect sizes
effectsize(Mr_mPF_nd)
effectsize(Mr_mPF_wd)

#create table with confidence intervals
ggpredict(Mr_mPF_nd, "temp")
ggpredict(Mr_mPF_wd, "distB2Mic")

```

#Plots 
#Myotis riparius
#Peak Frequency


```{r}

#Original plots
#M. riparius
pMrPF <- ggplot() + 
#geom_point(data=efMrPF_nd, aes(temp,fit)) + 
  geom_line(data=efMrPF_nd, aes(x=temp, y=fit), color="coral3", size=3) +
  #geom_point(data=efMrPF_nd, aes(x=temp, y=fit), color="black",size=2) +
  geom_ribbon(data=efMrPF_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)", y="Peak Frequency (kHz)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMrPF <- pMrPF + geom_point(data=GLM_Mr30, aes(temp,PF_E12), size=1.5,colour="coral3") + 
  xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
Mr_PF <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMrPF.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mr_PF, plot = pMrPF, dpi = 300, width = 15, height = 10, units = "cm")

```

#Models 
#Myotis riparius
#Source Level

```{r}

#Source Level
Mr_mSL_nd <- lmer(rmsSL_E12_10cm ~ temp + (temp|Ind), data=GLM_Mr30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope
Mr_mSL_wd <- lmer(rmsSL_E12_10cm ~ temp * distB2Mic + (temp|Ind), data=GLM_Mr30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope


#Random slope models summary
coef(Mr_mSL_nd)
summary(Mr_mSL_nd)
anova(Mr_mSL_nd)
#Random slope models summary
coef(Mr_mSL_wd)
summary(Mr_mSL_wd)
anova(Mr_mSL_wd)

tab_model(Mr_mSL_nd, Mr_mSL_wd,show.aic = TRUE) #compare models in one single table

efMrSLm_nd <- effect("temp", Mr_mSL_nd)
efMrSLm_nd <- as.data.frame(efMrSLm_nd)
efMrSLm_nd

efMrSLm_wd <- effect("temp", Mr_mSL_wd)
efMrSLm_wd <- as.data.frame(efMrSLm_wd)
efMrSLm_wd

#Effect sizes
effectsize(Mr_mSL_nd)
effectsize(Mr_mSL_wd)

#create table with confidence intervals
ggpredict(Mr_mSL_nd, "temp")
ggpredict(Mr_mSLwd, "temp")

```


#Plots 
#Myotis riparius
#Source Level


```{r}


#Original plots
#M. riparius
pMrSL <- ggplot() + 
#geom_point(data=efMrSLm_nd, aes(temp,fit)) + 
  geom_line(data=efMrSLm_nd, aes(x=temp, y=fit), color="coral3", size=3) +
  #geom_point(data=efMrSLm_nd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efMrSLm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)", y="apSL (dB@10cm_re20µPa)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMrSL <- pMrSL + geom_point(data=GLM_Mr30, aes(temp,rmsSL_E12_10cm), size=1.5,colour="coral3") + xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
Mr_SL <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMrSL.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mr_SL, plot = pMrSL, dpi = 300, width = 15, height = 10, units = "cm")

```

#Models 
#Myotis riparius
#Duration

```{r}
#Duration

Mr_mDur_nd <- lmer(dur_E12 ~ temp + (temp|Ind), data=GLM_Mr30, REML = F,
                 control = lmerControl(optimizer ="Nelder_Mead"))
Mr_mDur_wd <- lmer(dur_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mr30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope


#Random slope models summary
coef(Mr_mDur_nd)
summary(Mr_mDur_nd)
anova(Mr_mDur_nd)

#Random slope models summary
coef(Mr_mDur_wd)
summary(Mr_mDur_wd)
anova(Mr_mDur_wd)

tab_model(Mr_mDur_nd, Mr_mDur_wd,show.aic = TRUE) #compare models in one single table

##
efMrDurm_nd <- effect("temp", Mr_mDur_nd)
efMrDurm_nd <- as.data.frame(efMrDurm_nd)
efMrDurm_nd
##
efMrDurm_wd <- effect("temp", Mr_mDur_wd)
efMrDurm_wd <- as.data.frame(efMrDurm_wd)
efMrDurm_wd


#Effect sizes
effectsize(Mr_mDur_nd)
effectsize(Mr_mDur_wd)

#create table with confidence intervals
ggpredict(Mr_mDur_nd, "temp")
ggpredict(Mr_mDur_wd, "temp")

```

#Plots 
#Myotis riparius
#Duration


```{r}

#Original plots
#M. riparius
pMrDur <- ggplot() + 
#geom_point(data=efMrDurm_nd, aes(temp,fit)) + 
  geom_line(data=efMrDurm_nd, aes(x=temp, y=fit), color="coral3", size=3) +
  #geom_point(data=efMrDurm_nd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efMrDurm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)",y="Duration (ms)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMrDur <- pMrDur + geom_point(data=GLM_Mr30, aes(temp,dur_E12), size=1.5,colour="coral3")+ 
  xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
Mr_Dur <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMrDur.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mr_Dur, plot = pMrDur, dpi = 300, width = 15, height = 10, units = "cm")

```

#Models 
#Myotis group
#Peak Frequency

```{r}

Mg_mPF_nd <- lmer(PF_E12 ~ temp + (temp|Ind), data=GLM_Mg30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope
Mg_mPF_wd <- lmer(PF_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mg30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope

#Random slope models summary
coef(Mg_mPF_nd)
summary(Mg_mPF_nd)
anova(Mg_mPF_nd)

#Random slope models summary
coef(Mg_mPF_wd)
summary(Mg_mPF_wd)
anova(Mg_mPF_wd)


tab_model(Mg_mPF_nd, Mg_mPF_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efMgPFm_nd <- effect("temp", Mg_mPF_nd)
efMgPFm_nd <- as.data.frame(efMgPFm_nd)
efMgPFm_nd

efMgPFm_wd <- effect("temp", Mg_mPF_wd)
efMgPFm_wd <- as.data.frame(efMgPFm_wd)
efMgPFm_wd

#Effect sizes
effectsize(Mg_mPF_nd)
effectsize(Mg_mPF_wd)

#create table with confidence intervals
ggpredict(Mg_mPF_nd, "temp")
ggpredict(Mg_mPF_wd, "distB2Mic")

```

#Plots 
#Myotis group
#Peak Frequency


```{r}

#Original plots
#M. nigricans/elegans (Mg)
pMgPF <- ggplot() + 
#geom_point(data=efMgPFm_nd, aes(temp,fit)) + 
  geom_line(data=efMgPFm_nd, aes(x=temp, y=fit), color="darkgoldenrod1", size=3) +
  #geom_point(data=efMgPFm_nd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efMgPFm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)",y="Peak Frequency (kHz)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMgPF <- pMgPF + geom_point(data=GLM_Mg30, aes(temp,PF_E12), size=1.5,colour="darkgoldenrod1")+ 
xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
Mg_PF <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMgPF.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mg_PF, plot = pMgPF, dpi = 300, width = 15, height = 10, units = "cm")

```


#Models 
#Myotis group
#Source Level

```{r}

#Source Level
Mg_mSL_nd <- lmer(rmsSL_E12_10cm ~ temp + (temp|Ind), data=GLM_Mg30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope
Mg_mSL_wd <- lmer(rmsSL_E12_10cm ~ temp * distB2Mic + (temp|Ind), data=GLM_Mg30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope

#Random slope models summary
coef(Mg_mSL_nd)
summary(Mg_mSL_nd)
anova(Mg_mSL_nd)

#Random slope models summary
coef(Mg_mSL_wd)
summary(Mg_mSL_wd)
anova(Mg_mSL_wd)


tab_model(Mg_mSL_nd, Mg_mSL_wd,show.aic = TRUE) #compare models in one single table

efMgSLm_nd <- effect("temp", Mg_mSL_nd)
efMgSLm_nd <- as.data.frame(efMgSLm_nd)
efMgSLm_nd

efMgSLm_wd <- effect("temp", Mg_mSL_wd)
efMgSLm_wd <- as.data.frame(efMgSLm_wd)
efMgSLm_wd

#Effect sizes
effectsize(Mg_mSL_nd)
effectsize(Mg_mSL_wd)

#create table with confidence intervals
ggpredict(Mg_mSL_nd, "temp")
ggpredict(Mg_mSL_wd, "temp")

```


#Plots 
#Myotis group
#Source Level


```{r}

#Original plots
# M.nigricans/elegans (Mg)
pMgSL <- ggplot() + 
#geom_point(data=efMgSLm_nd, aes(temp,fit)) + 
  geom_line(data=efMgSLm_nd, aes(x=temp, y=fit), color="darkgoldenrod1", size=3) +
  #geom_point(data=efMgSLm_nd, aes(x=temp, y=fit), color="black", size = 2) +
  geom_ribbon(data=efMgSLm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)",y="apSL (dB@10cm_re20µPa)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMgSL <- pMgSL + geom_point(data=GLM_Mg30, aes(temp,rmsSL_E12_10cm), 
                            size=1.5, colour="darkgoldenrod1")+
  xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
Mg_SL <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMgSL.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mg_SL, plot = pMgSL, dpi = 300, width = 15, height = 10, units = "cm")

```


#Models 
#Myotis group
#Duration

```{r}
#Duration

Mg_mDur_nd <- lmer(dur_E12 ~ temp + (temp|Ind), data=GLM_Mg30, REML = F,
                 control = lmerControl(optimizer ="Nelder_Mead"))
Mg_mDur_wd <- lmer(dur_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Mg30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope

#Random slope models summary
coef(Mg_mDur_nd)
summary(Mg_mDur_nd)
anova(Mg_mDur_nd)

#Random slope models summary
coef(Mg_mDur_wd)
summary(Mg_mDur_wd)
anova(Mg_mDur_wd)


tab_model(Mg_mDur_nd, Mg_mDur_wd,show.aic = TRUE) #compare models in one single table

##
efMgDurm_nd <- effect("temp", Mg_mDur_nd)
efMgDurm_nd <- as.data.frame(efMgDurm_nd)
efMgDurm_nd
##
efMgDurm_wd <- effect("temp", Mg_mDur_wd)
efMgDurm_wd <- as.data.frame(efMgDurm_wd)
efMgDurm_wd

#Effect sizes
effectsize(Mg_mDur_nd)
effectsize(Mg_mDur_wd)

#create table with confidence intervals
ggpredict(Mg_mDur_nd, "temp")
ggpredict(Mg_mDur_wd, "temp")

```

#Plots 
#Myotis group
#Duration

```{r}

#Original plots
#M. nigricans/elegans
pMgDur <- ggplot() + 
#geom_point(data=efMgDurm_nd, aes(temp,fit)) + 
  geom_line(data=efMgDurm_nd, aes(x=temp, y=fit), color="darkgoldenrod1", size=3) +
  #geom_point(data=efMgDurm_nd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efMgDurm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)",y="Duration (ms)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pMgDur <- pMgDur + geom_point(data=GLM_Mg30, aes(temp,dur_E12),size=1.5,colour="darkgoldenrod1")+
xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
Mg_Dur <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pMgDur.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mg_Dur, plot = pMgDur, dpi = 300, width = 15, height = 10, units = "cm")


```

#Models 
#Eptesicus brasiliensis
#Peak Frequency

```{r}

Eb_mPF_nd <- lmer(PF_E12 ~ temp + (temp|Ind), data=GLM_Eb30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope
Eb_mPF_wd <- lmer(PF_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Eb30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope

#Random slope models summary
coef(Eb_mPF_nd)
summary(Eb_mPF_nd)
anova(Eb_mPF_nd)

#Random slope models summary
coef(Eb_mPF_wd)
summary(Eb_mPF_wd)
anova(Eb_mPF_wd)

tab_model(Eb_mPF_nd, Eb_mPF_wd,show.aic = TRUE) #compare models in one single table

# make effect table
efEbPFm_nd <- effect("temp", Eb_mPF_nd)
efEbPFm_nd <- as.data.frame(efEbPFm_nd)
efEbPFm_nd

efEbPFm_wd <- effect("temp", Eb_mPF_wd)
efEbPFm_wd <- as.data.frame(efEbPFm_wd)
efEbPFm_wd

#Effect sizes
effectsize(Eb_mPF_nd)
effectsize(Eb_mPF_wd)

#create table with confidence intervals
ggpredict(Eb_mPF_nd, "temp")
ggpredict(Eb_mPF_wd, "distB2Mic")

```

#Plots 
#Eptesicus brasiliensis
#Peak Frequency


```{r}


#Original plots

pEbPF <- ggplot() + 
#geom_point(data=efEbPFm_nd, aes(temp,fit)) + 
  geom_line(data=efEbPFm_nd, aes(x=temp, y=fit), color="dodgerblue2", size=3) +
  #geom_point(data=efEbPFm_nd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efEbPFm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)", y="Peak Frequency (kHz)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))


pEbPF <- pEbPF + geom_point(data=GLM_Eb30, aes(temp,PF_E12), size=1.5,colour="dodgerblue2") + 
  xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
EbPF <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pEbPF.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = EbPF, plot = pEbPF, dpi = 300, width = 15, height = 10, units = "cm")


```

#Models 
#Eptesicus brasiliensis
#Source Level

```{r}

#Source Level
Eb_mSL_nd <- lmer(rmsSL_E12_10cm ~ temp + (temp|Ind), data=GLM_Eb30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope
Eb_mSL_wd <- lmer(rmsSL_E12_10cm ~ temp * distB2Mic + (temp|Ind), data=GLM_Eb30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope

#Random slope models summary
coef(Eb_mSL_nd)
summary(Eb_mSL_nd)
anova(Eb_mSL_nd)
#Random slope models summary
coef(Eb_mSL_wd)
summary(Eb_mSL_wd)
anova(Eb_mSL_wd)

tab_model(Eb_mSL_nd, Eb_mSL_wd,show.aic = TRUE) #compare models in one single table

efEbSLm_nd <- effect("temp", Eb_mSL_nd)
efEbSLm_nd <- as.data.frame(efEbSLm_nd)
efEbSLm_nd

efEbSLm_wd <- effect("temp", Eb_mSL_wd)
efEbSLm_wd <- as.data.frame(efEbSLm_wd)
efEbSLm_wd

#Effect sizes
effectsize(Eb_mSL_nd)
effectsize(Eb_mSL_wd)

#create table with confidence intervals
ggpredict(Eb_mSL_nd, "temp")
ggpredict(Eb_mSL_wd, "temp")

```


#Plots 
#Eptesicus brasiliensis
#Source Level

```{r}

#Original plots 
pEbSL <- ggplot() + 
#geom_point(data=efEbSLm_nd, aes(temp,fit)) + 
  geom_line(data=efEbSLm_nd, aes(x=temp, y=fit), color="dodgerblue2", size=3) +
  #geom_point(data=efEbSLm_nd, aes(x=temp, y=fit), color="black", size = 2) +
  geom_ribbon(data=efEbSLm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)", y="apSL (dB@10cm_re20µPa)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))

pEbSL <- pEbSL + geom_point(data=GLM_Eb30, aes(temp,rmsSL_E12_10cm),size=1.5,color="dodgerblue2") + xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
EbSL <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pEbSL.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = EbSL, plot = pEbSL, dpi = 300, width = 15, height = 10, units = "cm")

```


#Models 
#Eptesicus brasiliensis
#Duration

```{r}
#Duration

Eb_mDur_nd <- lmer(dur_E12 ~ temp + (temp|Ind), data=GLM_Eb30, REML = F,
                 control = lmerControl(optimizer ="Nelder_Mead"))
Eb_mDur_wd <- lmer(dur_E12 ~ temp * distB2Mic + (temp|Ind), data=GLM_Eb30, REML = F,
                control = lmerControl(optimizer ="Nelder_Mead")) # random slope

#Random slope models summary
coef(Eb_mDur_nd)
summary(Eb_mDur_nd)
anova(Eb_mDur_nd)
#Random slope models summary
coef(Eb_mDur_wd)
summary(Eb_mDur_wd)
anova(Eb_mDur_wd)

tab_model(Eb_mDur_nd, Eb_mDur_wd,show.aic = TRUE) #compare models in one single table

##
efEbDurm_nd <- effect("temp", Eb_mDur_nd)
efEbDurm_nd <- as.data.frame(efEbDurm_nd)
efEbDurm_nd
##
efEbDurm_wd <- effect("temp", Eb_mDur_wd)
efEbDurm_wd <- as.data.frame(efEbDurm_wd)
efEbDurm_wd

#Effect sizes
effectsize(Eb_mDur_nd)
effectsize(Eb_mDur_wd)

#create table with confidence intervals
ggpredict(Eb_mDur_nd, "temp")
ggpredict(Eb_mDur_wd, "temp")

```

#Plots 
#Eptesicus brasiliensis
#Duration

```{r}

#Original plots
pEbDur <- ggplot() + 
#geom_point(data=efEbDurm_nd, aes(temp,fit)) +
  geom_line(data=efEbDurm_nd, aes(x=temp, y=fit), color="dodgerblue2", size=3) +
  #geom_point(data=efEbDurm_nd, aes(x=temp, y=fit), color="black", size=2) +
  geom_ribbon(data=efEbDurm_nd, aes(x=temp, ymin=lower, ymax=upper), alpha= 0.3, fill="grey") +
  labs(x="Temperature (°C)", y="Duration (ms)")+
  theme_bw() + theme(axis.title=element_text(size=14,face="bold"),
                     axis.text=element_text(size=14))


pEbDur <- pEbDur + geom_point(data=GLM_Eb30, aes(temp,dur_E12), size=1.5,colour="dodgerblue2") + 
  xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14), 
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))

# Definir la ruta y el nombre del archivo
EbDur <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/pEbDur.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = EbDur, plot = pEbDur, dpi = 300, width = 15, height = 10, units = "cm")


```


# Models to evaluate the effect of temperature on Atmospheric Attenuation
#M.oxyotus

```{r}
#Make data frame with the two types of AA in one single column. 
colnames(GLM_Mo30)
#Separate data frames
AAFp_Mo <- GLM_Mo30[c(1:13,26,60)] # column 60 is AAFp (atmospheric attenuation with observed values)
names(AAFp_Mo)[15]<-paste("AA")
AAFp_Mo$AAtype <- "AAFp"

AAmeanFp_Mo <- GLM_Mo30[c(1:13,26,61)] #column 60 is AAmeanFp (AA with theoric values)
names(AAmeanFp_Mo)[15]<-paste("AA")
AAmeanFp_Mo$AAtype <- "AAmean"

AA_Mo <- rbind(AAFp_Mo,AAmeanFp_Mo) #bind dataframes: AA in one column and AAtype in anohter
nrow(AAFp_Mo)
nrow(AA_Mo) #check nrow to be sure that the number of rows match correctly


#make interaction model
Mo_AAtype_nd <- lmer(AA ~ AAtype * temp + (temp|Ind), data=AA_Mo, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model no distance
Mo_AAtype_wd <- lmer(AA ~ AAtype * temp * distB2Mic + (temp|Ind), data=AA_Mo, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model with distance


# make effect table only for the model selected
Mo_tAA_nd = sjPlot:: tab_model(Mo_AAtype_nd)
Mo_tAAm_wd = sjPlot:: tab_model(Mo_AAtype_wd)

tab_model(Mo_AAtype_nd, Mo_AAtype_wd,show.aic = TRUE) #compare models in one single table

```

#Plot temperature vs AA 
#Myotis oxyotus2D

```{r}
colnames(AA_Mo)

# Separate the dataframe into two based on AAtype
AAFp_Mo <- subset(AA_Mo, AAtype == "AAFp")
AAmean_Mo <- subset(AA_Mo, AAtype == "AAmean")


# Function to generate predictions for grid values
generate_predictions <- function(model, data, temp_seq, dist_seq) {
  grid <- expand.grid(temp = temp_seq, distB2Mic = dist_seq)
  grid$AAtype <- unique(data$AAtype) # Ensure the correct AAtype is used
  grid$Ind <- NA # Placeholder, if required by the model
  
  # Predict using the model and new data
  grid$pred_AA <- predict(model, newdata = grid, re.form = NA)
  return(grid)
}

# Generate temperature and distance sequences for AAFp
tr_AAFp_Mo <- seq(min(AAFp_Mo$temp), max(AAFp_Mo$temp), length.out = 30)
dr_AAFp_Mo <- seq(min(AAFp_Mo$distB2Mic), max(AAFp_Mo$distB2Mic), length.out = 30)

# Generate predictions for AAFp
gr_AAFp_Mo_wd <- generate_predictions(Mo_AAtype_wd, AAFp_Mo, tr_AAFp_Mo, dr_AAFp_Mo)


col_palette <- rev(viridis::viridis(30))  # Reverse the viridis color palette


#AAmean

# Generate temperature and distance sequences for AAmean
tr_AAmean_Mo <- seq(min(AAmean_Mo$temp), max(AAmean_Mo$temp), length.out = 30)
dr_AAmean_Mo <- seq(min(AAmean_Mo$distB2Mic), max(AAmean_Mo$distB2Mic), length.out = 30)

# Generate predictions for AAmean
gr_AAmean_Mo_wd <- generate_predictions(Mo_AAtype_wd, AAmean_Mo, tr_AAmean_Mo, dr_AAmean_Mo)


#OPTION 2

# Plot image with discrete colors
pMo_AAFp_wd <- ggplot(gr_AAFp_Mo_wd, aes(x = temp, y = distB2Mic, fill = cut(pred_AA, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "AAFp") +
  scale_fill_manual(values = colors) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold")  # Increase y-axis title size
  )


  # Definir la ruta y el nombre del archivo
pMo_AAFp_wd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mo2D_AAFP.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mo2D_AAFP, plot = p2Mo_AAFp2, dpi = 300, width = 15, height = 10, units = "cm")

pMo_AAmean_wd <- ggplot(gr_AAmean_Mo_wd, aes(x = temp, y = distB2Mic, fill = cut(pred_AA, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "AAmean") +
  scale_fill_manual(values = colors) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold")  # Increase y-axis title size
  )

  # Definir la ruta y el nombre del archivo
pMo_AAmean_wd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mo2D_AAmean.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mo2D_AAmean, plot = p2Mo_AAmean2, dpi = 300, width = 15, height = 10, units = "cm")


```


# Models to evaluate the effect of temperature on Atmospheric Attenuation
#M.pilosatibiais

```{r}
#Make data frame with the two types of AA in one single column. 
colnames(GLM_Mk30)
#Separate data frames
AAFp_Mk <- GLM_Mk30[c(1:13,26,60)] # column 60 is AAFp (atmospheric attenuation with observed values)
names(AAFp_Mk)[15]<-paste("AA")
AAFp_Mk$AAtype <- "AAFp"

AAmeanFp_Mk <- GLM_Mk30[c(1:13,26,61)] #column 60 is AAmeanFp (AA with theoric values)
names(AAmeanFp_Mk)[15]<-paste("AA")
AAmeanFp_Mk$AAtype <- "AAmean"

AA_Mk <- rbind(AAFp_Mk,AAmeanFp_Mk) #bind dataframes: AA in one column and AAtype in anohter
nrow(AAFp_Mk)
nrow(AA_Mk) #check nrow to be sure that the number of rows match correctly

#Filter data bellow 1.5 in distance 
filt_AA_Mk <- subset(AA_Mk, distB2Mic >= 1.5)
nrow(AA_Mk)
nrow(filt_AA_Mk)

#make interaction model
Mk_AAtype_nd <- lmer(AA ~ AAtype * temp + (temp|Ind), data=AA_Mk, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model no distance
Mk_AAtype_wd <- lmer(AA ~ AAtype * temp * distB2Mic + (temp|Ind), data=AA_Mk, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model with distance


# make effect table only for the model selected
Mk_tAA_nd = sjPlot:: tab_model(Mk_AAtype_nd)
Mk_tAAm_wd = sjPlot:: tab_model(Mk_AAtype_wd)

tab_model(Mk_AAtype_nd, Mk_AAtype_wd,show.aic = TRUE) #compare models in one single table

```

# Plot AA vs Temp
#M.pilosatibialis

```{r}

colnames(AA_Mk)

# Separate the dataframe into two based on AAtype
AAFp_Mk <- subset(AA_Mk, AAtype == "AAFp")
AAmean_Mk <- subset(AA_Mk, AAtype == "AAmean")


# Function to generate predictions for grid values
generate_predictions <- function(model, data, temp_seq, dist_seq) {
  grid <- expand.grid(temp = temp_seq, distB2Mic = dist_seq)
  grid$AAtype <- unique(data$AAtype) # Ensure the correct AAtype is used
  grid$Ind <- NA # Placeholder, if required by the model
  
  # Predict using the model and new data
  grid$pred_AA <- predict(model, newdata = grid, re.form = NA)
  return(grid)
}

# Generate temperature and distance sequences
tr_AAFp_Mk <- seq(min(AAFp_Mk$temp), max(AAFp_Mk$temp), length.out = 30)
dr_AAFp_Mk <- seq(min(AAFp_Mk$distB2Mic), max(AAFp_Mk$distB2Mic), length.out = 30)

# Generate predictions for AAFp
gr_AAFp_Mk_wd <- generate_predictions(Mk_AAtype_wd, AAFp_Mk, tr_AAFp_Mk, dr_AAFp_Mk)

# Generate temperature and distance sequences for AAmean
tr_AAmean_Mk <- seq(min(AAmean_Mk$temp), max(AAmean_Mk$temp), length.out = 30)
dr_AAmean_Mk <- seq(min(AAmean_Mk$distB2Mic), max(AAmean_Mk$distB2Mic), length.out = 30)

# Generate predictions for AAmean
gr_AAmean_Mk_wd <- generate_predictions(Mk_AAtype_wd, AAmean_Mk, tr_AAmean_Mk, dr_AAmean_Mk)

gr_combined_Mk_wd <- rbind(
  transform(gr_AAFp_Mk_wd, AAtype = "AAFp"),
  transform(gr_AAmean_Mk_wd, AAtype = "AAmean")
)


p_Mk_combined <- ggplot(gr_combined_Mk, aes(x = temp, y = distB2Mic, fill = cut(pred_AA, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "Combined AA") +
  scale_fill_manual(values = colors) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold"),  # Increase y-axis title size
    legend.position = "none"
  )

print(p_Mk_combined)
# Definir la ruta y el nombre del archivo
p_Mk_combined <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mk2D_AA.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mk2D_AA, plot = p_combined, dpi = 300, width = 15, height = 10, units = "cm")


```


# Models to evaluate the effect of temperature on Atmospheric Attenuation
#M.riparius

```{r}
#Make data frame with the two types of AA in one single column. 
colnames(GLM_Mr30)
#Separate data frames
AAFp_Mr <- GLM_Mr30[c(1:13,26,60)] # column 60 is AAFp (atmospheric attenuation with observed values)
names(AAFp_Mr)[15]<-paste("AA")
AAFp_Mr$AAtype <- "AAFp"

AAmeanFp_Mr <- GLM_Mr30[c(1:13,26,61)] #column 60 is AAmeanFp (AA with theoric values)
names(AAmeanFp_Mr)[15]<-paste("AA")
AAmeanFp_Mr$AAtype <- "AAmean"

AA_Mr <- rbind(AAFp_Mr,AAmeanFp_Mr) #bind dataframes: AA in one column and AAtype in anohter
nrow(AAFp_Mr)
nrow(AA_Mr) #check nrow to be sure that the number of rows match correctly

#Filter data bellow 1.5 in distance 
filt_AA_Mr <- subset(AA_Mr, distB2Mic >= 1.5)
nrow(AA_Mr)
nrow(filt_AA_Mr)

#make interaction model
Mr_AAtype_nd <- lmer(AA ~ AAtype * temp + (temp|Ind), data=AA_Mr, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model no distance 
Mr_AAtype_wd <- lmer(AA ~ AAtype * temp * distB2Mic + (temp|Ind), data=AA_Mr, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model with distance


#model_nd
coef(Mr_AAtype_nd)
anova(Mr_AAtype_nd)
summary(Mr_AAtype_nd)
#model_wd
coef(Mr_AAtype_wd)
anova(Mr_AAtype_wd)
summary(Mr_AAtype_wd)

# make effect table only for the model selected
Mr_tAA_nd = sjPlot:: tab_model(Mr_AAtype_nd)
Mr_tAA_wd = sjPlot:: tab_model(Mr_AAtype_wd)

tab_model(Mr_AAtype_nd, Mr_AAtype_wd,show.aic = TRUE) #compare models in one single table

```

# Plot AA vs Temp
#M.riparius

```{r}

pMrAA_wd <- interact_plot(Mr_AAtype_wd, pred = temp, modx = AAtype,interval = TRUE,int.width = 0.95,
              vary.lty = FALSE,
              plot.points = TRUE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "AAref",
              colors = c("coral3","gray47"),
              line.thickness = 2,
              modx.labels = c("Experimental model","Ambient model"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)


pMrAA_wd <- pMrAA + xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()

# Definir la ruta y el nombre del archivo
pMrAA_wd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/Mr_AA.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mr_AA, plot = pMrAA, dpi = 300, width = 15, height = 10, units = "cm") 


```


# Models to evaluate the effect of temperature on Atmospheric Attenuation
#M.group

```{r}
#Make data frame with the two types of AA in one single column. 
colnames(GLM_Mg30)
#Separate data frames
AAFp_Mg <- GLM_Mg30[c(1:13,26,60)] # column 60 is AAFp (atmospheric attenuation with observed values)
names(AAFp_Mg)[15]<-paste("AA")
AAFp_Mg$AAtype <- "AAFp"

AAmeanFp_Mg <- GLM_Mg30[c(1:13,26,61)] #column 60 is AAmeanFp (AA with theoric values)
names(AAmeanFp_Mg)[15]<-paste("AA")
AAmeanFp_Mg$AAtype <- "AAmean"

AA_Mg <- rbind(AAFp_Mg,AAmeanFp_Mg) #bind dataframes: AA in one column and AAtype in anohter
nrow(AAFp_Mg)
nrow(AA_Mg) #check nrow to be sure that the number of rows match correctly


#make interaction model
Mg_AAtype_nd <- lmer(AA ~ AAtype * temp + (temp|Ind), data=AA_Mg, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model
Mg_AAtype_wd <- lmer(AA ~ AAtype * temp * distB2Mic + (temp|Ind), data=AA_Mg, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model


coef(Mg_AAtype_nd)
anova(Mg_AAtype_nd)
summary(Mg_AAtype_nd)
#model4
coef(Mg_AAtype_wd)
anova(Mg_AAtype_wd)
summary(Mg_AAtype_wd)

# make effect table only for the model selected
Mg_tAAm_nd = sjPlot:: tab_model(Mg_AAtype_nd)
Mg_tAAm_wd = sjPlot:: tab_model(Mg_AAtype_wd)

tab_model(Mg_m2AAtype, Mg_m4AAtype,show.aic = TRUE) #compare models in one single table

```

# Plot AA vs Temp
#M.group

```{r}

pMgAA <- interact_plot(Mg_AAtype_nd, pred = temp, modx = AAtype,interval = TRUE,int.width = 0.6,
              vary.lty = FALSE,
              plot.points = TRUE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "AAref",
              colors = c("darkgoldenrod1","gray47"),
              line.thickness = 2,
              modx.labels = c("Experimental model","Ambient model"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)


pMgAA <- pMgAA + xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()

# Definir la ruta y el nombre del archivo
Mg_AA <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/Mg_AA.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mg_AA, plot = pMgAA, dpi = 300, width = 15, height = 10, units = "cm") 


```


# Models to evaluate the effect of temperature on Atmospheric Attenuation
#E. brasiliensis

```{r}
#Make data frame with the two types of AA in one single column. 
colnames(GLM_Eb30)
#Separate data frames
AAFp_Eb <- GLM_Eb30[c(1:13,26,60)] # column 60 is AAFp (atmospheric attenuation with observed values)
names(AAFp_Eb)[15]<-paste("AA")
AAFp_Eb$AAtype <- "AAFp"

AAmeanFp_Eb <- GLM_Eb30[c(1:13,26,61)] #column 60 is AAmeanFp (AA with theoric values)
names(AAmeanFp_Eb)[15]<-paste("AA")
AAmeanFp_Eb$AAtype <- "AAmean"

AA_Eb <- rbind(AAFp_Eb,AAmeanFp_Eb) #bind dataframes: AA in one column and AAtype in anohter
nrow(AAFp_Eb)
nrow(AA_Eb) #check nrow to be sure that the number of rows match correctly

#make interaction model
Eb_AAtype_nd <- lmer(AA ~ AAtype * temp + (temp|Ind), data=AA_Eb, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model
Eb_AAtype_wd <- lmer(AA ~ AAtype * temp * distB2Mic + (temp|Ind), data=AA_Eb, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) #random slope model

#model2
coef(Eb_AAtype_nd)
anova(Eb_AAtype_nd)
summary(Eb_AAtype_nd)
#model4
coef(Eb_AAtype_wd)
anova(Eb_AAtype_wd)
summary(Eb_AAtype_wd)

# make effect table only for the model selected
Eb_tAAm_nd = sjPlot:: tab_model(Eb_AAtype_nd)
Eb_tAAm_wd = sjPlot:: tab_model(Eb_AAtype_wd)

tab_model(Eb_AAtype_nd, Eb_AAtype_wd,show.aic = TRUE) #compare models in one single table


```

# Plot AA vs Temp
#E. brasiliensis

```{r}

pEbAA <- interact_plot(Eb_AAtype_nd, pred = temp, modx = AAtype,interval = TRUE,int.width = 0.6,
              vary.lty = FALSE,
              plot.points = TRUE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "AAref",
              colors = c("dodgerblue2","gray47"),
              line.thickness = 2,
              modx.labels = c("Experimental model","Ambient model"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)


pEbAA <- pEbAA + xlim(18, 25) + 
  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()

# Definir la ruta y el nombre del archivo
Eb_AA <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/Eb_AA.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Eb_AA, plot = pEbAA, dpi = 300, width = 15, height = 10, units = "cm") 

```


# Detection Distance vs Temperature
# Myotis oxyotus 

```{r}

#TS -30
colnames(GLM_Mo30)
#avrg
avrgDD_Mo <- GLM_Mo30[c(1:13,26,66)] # column 66 correspond to avrg DD (theoric values)
names(avrgDD_Mo)[15]<-paste("DD")
avrgDD_Mo$DDtype <- "avrgDD"
#realDD2
realDD2_Mo <- GLM_Mo30[c(1:13,26,67)]
names(realDD2_Mo)[15]<-paste("DD") # column 67 correspond to realDD2 (observed values)
realDD2_Mo$DDtype <- "realDD2"

DD_Mo <- rbind(avrgDD_Mo,realDD2_Mo) #bind dataframes
head(DD_Mo)


#make models for average and observed parameters (non-responsive vs responsive bat)
Mo_DDtype_nd <- lmer(DD ~ DDtype * temp + (temp|Ind), data=DD_Mo, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))
Mo_DDtype_wd <- lmer(DD ~ DDtype * temp * distB2Mic + (temp|Ind), data=DD_Mo, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead")) 

#Model - no distance
coef(Mo_DDtype_nd)
anova(Mo_DDtype_nd)
summary(Mo_DDtype_nd)
#model - with distance
coef(Mo_DDtype_wd)
anova(Mo_DDtype_wd)
summary(Mo_DDtype_wd)

#Random slope summary table
Mo_tDD_nd = sjPlot:: tab_model(Mo_DDtype_nd)
#Random slope summary table
Mo_tDD_wd = sjPlot:: tab_model(Mo_DDtype_wd)

tab_model(Mo_DDtype_wd, Mo_DDtype_wd,show.aic = TRUE) #compare models in one single table

#Effect sizes
effectsize(Mo_DDtype_nd)
effectsize(Mo_DDtype_wd)

#create table with confidence intervals
ggeffect(Mo_DDtype_nd, "temp", ci_level = 0.95)
ggpredict(Mo_DDtype_nd, "temp", ci_level = 0.95)
#create table with confidence intervals
ggeffect(Mo_DDtype_wd, "temp", ci_level = 0.95)
ggpredict(Mo_DDtype_wd, "temp", ci_level = 0.95)


#create table with confidence intervals
resultMo_DD_nd <- ggpredict(Mo_DDtype_nd, c("temp","DDtype"))
resultMo_DD_nd
#create table with confidence intervals
resultMo_mDD_wd <- ggpredict(Mo_DDtype_wd, c("temp","DDtype"))
resultMo_mDD_wd

```

# Plot Detection Distance * temperature per species 

```{r}
#M.oxyotus
#TS -30
pMoDD30 <- interact_plot(Mo_DDtype_wd, pred = temp, modx = DDtype, interval = TRUE,
              line.thickness = 2,
              plot.points = TRUE,
              point.alpha = 1,
              point.size = 1,
              vary.lty = FALSE,
              int.width = 0.95,x.label = "Temperature (°C)", y.label = "Detection Distance (m)",
              legend.main = "DDref",
              colors = c("gray47","darkolivegreen4"),
              modx.labels = c("Ambient model","Experimental model"))+ 
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

pMoDD30 + xlim(18, 25)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14))


```

# Detection Ranges vs Temperature
#Tables
# Myotis pilosatibialis 

```{r}

#TS -30
colnames(GLM_Mk30)
#avrg
avrgDD_Mk <- GLM_Mk30[c(1:13,26,66)] # column 65 correspond to avrg DD (theoric values)
names(avrgDD_Mk)[15]<-paste("DD")
avrgDD_Mk$DDtype <- "avrgDD"
#realDD2
realDD2_Mk <- GLM_Mk30[c(1:13,26,67)]
names(realDD2_Mk)[15]<-paste("DD") # column 66 correspond to real DD (observed values)
realDD2_Mk$DDtype <- "realDD2"

DD_Mk <- rbind(avrgDD_Mk,realDD2_Mk) #bind dataframes
head(DD_Mk)


#make models for average and observed parameters (non-responsive vs responsive bat)
Mk_DDtype_nd <- lmer(DD ~ DDtype * temp + (temp|Ind), data=DD_Mk, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))
Mk_DDtype_wd <- lmer(DD ~ DDtype * temp * distB2Mic + (temp|Ind), data=DD_Mk, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))


#Random slope summary table
Mk_tDD_nd = sjPlot:: tab_model(Mk_DDtype_nd)
#Random slope summary table
Mk_tDD_wd = sjPlot:: tab_model(Mk_DDtype_wd)

tab_model(Mk_DDtype_nd, Mk_DDtype_wd,show.aic = TRUE) #compare models in one single table

#Effect sizes
effectsize(Mk_DDtype_nd)
effectsize(Mk_DDtype_wd)

#create table with confidence intervals
ggeffect(Mk_DDtype_nd, "temp", ci_level = 0.95)
ggpredict(Mk_DDtype_nd, "temp", ci_level = 0.95)
#create table with confidence intervals
ggeffect(Mk_DDtype_wd, "temp", ci_level = 0.95)
ggpredict(Mk_DDtype_wd, "temp", ci_level = 0.95)


#create table with confidence intervals
resultMk_DD_nd <- ggpredict(Mk_m2DDtype, c("temp","DDtype"))
resultMk_DD_nd
#create table with confidence intervals
resultMk_DD_wd <- ggpredict(Mk_m4DDtype, c("temp","DDtype"))
resultMk_DD_wd

```

# Plot Detection Distance * temperature per species 
#M.pilosatibialis

```{r}

#TS -30

# Extract predicted values from the model
predict_Mk_mDD_wd <- predict(Mk_DDtype_wd, newdata = DD_Mk, re.form = NA)

# Separate dataframe
DDreal_Mk <- subset(DD_Mk, DDtype == "realDD2")
DDavrg_Mk <- subset(DD_Mk, DDtype == "avrgDD")

# Generate predicted values for each combination of temperature and distance to microphone
#DDFP
tr_DDreal_Mk <- seq(min(DDreal_Mk$temp), max(DDreal_Mk$temp), length.out = 30)
dr_DDreal_Mk <- seq(min(DDreal_Mk$distB2Mic), max(DDreal_Mk$distB2Mic), length.out = 30)
pred_DDreal_Mk <- matrix(NA, nrow = length(tr_DDreal_Mk), ncol = length(dr_DDreal_Mk))

for (i in 1:length(tr_DDreal_Mk)) {
  for (j in 1:length(dr_DDreal_Mk)) {
    pred_DDreal_Mk[i, j] <- calculate_predicted(tr_DDreal_Mk[i], dr_DDreal_Mk[j])
  }
}

# Create data frame for plotting
gr_DDreal_Mk <- expand.grid(temp = tr_DDreal_Mk, distB2Mic = dr_DDreal_Mk)
gr_DDreal_Mk$pred_DDreal_Mk <- as.vector(pred_DDreal_Mk)

```


#read data frame with calculations of 20 TS

```{r}

Data_GLM20= read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_codes/AAA/DataWdist/AADD_20Wdist_thr1.csv", header = T, sep = ";")
Data_GLM20 <- as.data.frame(Data_GLM20[,-1])
colnames(Data_GLM20)
str(Data_GLM20)

Ind = as.data.frame(sprintf("%03d", Data_GLM20$Ind))
names(Ind)[1]<-paste("Ind")
Data_GLM20 <- cbind(Data_GLM20, Ind)
Data_GLM20 <- Data_GLM20[, c(1:2,74,4:73)]
Data_GLM20[, 'Ind'] <- as.factor(Data_GLM20[,'Ind'])
str(Data_GLM20)

i <- c(37:39)#create the i vector with the columns that I need to be numeric
Data_GLM20[ , i] <- apply(Data_GLM20[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10,11,73)#create the i vector with the columns that I need to be as.character

Data_GLM20[ , i] <- apply(Data_GLM20[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))

#make Date_Time column as.Date

Data_GLM20$Date_Time <- gsub('_', ' ', Data_GLM20$Date_Time) #deparate date and time by space
Data_GLM20$Date <- sapply(strsplit(as.character(Data_GLM20$Date_Time), " "), "[", 1) #make date 1 column
Data_GLM20$Time <- sapply(strsplit(as.character(Data_GLM20$Date_Time), " "), "[", 2) #make time 2 column
Data_GLM20$Time <- gsub('-', ':', Data_GLM20$Time) #change - for : for correct time format 
Data_GLM20$Date_Time <- as.POSIXct(paste(Data_GLM20$Date, Data_GLM20$Time), format="%Y-%m-%d %H:%M:%S") #make as.Date
Data_GLM20 <- Data_GLM20[,-c(74,75)] #delete columns of date and time that we don't need anymore. 

str(Data_GLM20)
nrow(Data_GLM20)
colnames(Data_GLM20)
head(Data_GLM20)

names(Data_GLM20)[names(Data_GLM20) == 'T'] <- 'temp'
colnames(Data_GLM20)

```

# Check Harmonic 

```{r}

#Check harmonic

Data_GLM20$Harmonic = case_when(
        Data_GLM20$Species=="M.oxyotus" & Data_GLM20$PF_E12 <=70 ~ "1st",
        Data_GLM20$Species=="M.keaysi" & Data_GLM20$PF_E12 <=85 ~ "1st", 
        Data_GLM20$Species=="M.riparius" & Data_GLM20$PF_E12 <=85 ~ "1st",
        Data_GLM20$Species=="M.albescens" & Data_GLM20$PF_E12 <=85 ~ "1st",
        Data_GLM20$Species=="M.elegans" & Data_GLM20$PF_E12 <=85 ~ "1st",
        Data_GLM20$Species=="M.nigricans" & Data_GLM20$PF_E12 <=80 ~ "1st",
        Data_GLM20$Species=="E.brasiliensis" & Data_GLM20$PF_E12 <=75 ~ "1st")

#Replace the NA's that does not belong to the previous condition with "2nd" (second harmonic)        
Data_GLM20$Harmonic [is.na(Data_GLM20$Harmonic )] <- "2nd"
Data_GLM20$Harmonic

Data_GLM20<- subset(Data_GLM20, Harmonic != "2nd") 
nrow(Data_GLM20)
colnames(Data_GLM20)


Data_GLM20 <- Data_GLM20[!is.na(Data_GLM20$distB2Mic),]
nrow(Data_GLM20)
colnames(Data_GLM20)

Data_GLM20 <- Data_GLM20 %>% 
  mutate(dist_cat = ifelse(distB2Mic < 1.5, "<1.5", ">1.5"))

length(which(Data_GLM20$dist_cat == "<1.5"))
length(which(Data_GLM20$dist_cat == ">1.5"))

```


# Separate dataset by species

```{r}
#Separate dataset by group of species
colnames(Data_GLM20)
GLM_Mo20 <- Data_GLM20[ which(Data_GLM20$GS=="M.oxyotus"),]
GLM_Mk20 <- Data_GLM20[ which(Data_GLM20$GS=="M.keaysi"),]
GLM_Mr20 <- Data_GLM20[ which(Data_GLM20$GS=="M.riparius"),]
GLM_Mg20 <- Data_GLM20[ which(Data_GLM20$GS=="M.group"),]
GLM_Eb20 <- Data_GLM20[ which(Data_GLM20$GS=="E.brasiliensis"),]


```


# Myotis oxyotus 

```{r}

#TS -20
colnames(GLM_Mo20)

#avrg
avrgDD_Mo20 <- GLM_Mo20[c(1:13,26,66)] # column 66 correspond to avrg DD (theoric values)
names(avrgDD_Mo20)[15]<-paste("DD")
avrgDD_Mo20$DDtype <- "avrgDD"
#realDD2
realDD2_Mo20 <- GLM_Mo20[c(1:13,26,67)]
names(realDD2_Mo20)[15]<-paste("DD") # column 67 correspond to real DD (observed values)
realDD2_Mo20$DDtype <- "realDD2"

DD_Mo20 <- rbind(avrgDD_Mo20,realDD2_Mo20) #bind dataframes
head(DD_Mo20)

#Filter data bellow 1.5 in distance 
filt_DD_Mo20 <- subset(DD_Mo20, distB2Mic >= 1.5)
head(filt_DD_Mo20)
nrow(DD_Mo20)
nrow(filt_DD_Mo20)

#make models for average and observed parameters (non-responsive vs responsive bat)
Mo20_DDtype_nd <- lmer(DD ~ DDtype * temp + (temp|Ind), data=DD_Mo20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))
Mo20_DDtype_wd <- lmer(DD ~ DDtype * temp * distB2Mic + (temp|Ind), data=DD_Mo20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))

#model_nd
coef(Mo20_DDtype_nd)
anova(Mo20_DDtype_nd)
summary(Mo20_DDtype_nd)
#model_wd
coef(Mo20_DDtype_wd)
anova(Mo20_DDtype_wd)
summary(Mo20_DDtype_wd)

#Random slope summary table
Mo20_tDDm_nd = sjPlot:: tab_model(Mo20_DDtype_nd)
#Random slope summary table
Mo20_tDDm_wf = sjPlot:: tab_model(Mo20_DDtype_wd)

tab_model(Mo20_DDtype_nd, Mo20_DDtype_wd,show.aic = TRUE) #compare models in one single table

#Effect sizes
effectsize(Mo20_DDtype_nd)
effectsize(Mo20_DDtype_wd)

#create table with confidence intervals
ggeffect(Mo20_DDtype_nd, "temp", ci_level = 0.95)
ggpredict(Mo20_DDtype_nd, "temp", ci_level = 0.95)
#create table with confidence intervals
ggeffect(Mo20_DDtype_wd, "temp", ci_level = 0.95)
ggpredict(Mo20_DDtype_wd, "temp", ci_level = 0.95)


#create table with confidence intervals
resultMo20_DDm_nd <- ggpredict(Mo20_DDtype_nd, c("temp","DDtype"))
resultMo20_DDm_nd
#create table with confidence intervals
resultMo20_DDm_wd <- ggpredict(Mo20_DDtype_wd, c("temp","DDtype"))
resultMo20_DDm_wd

```


# Plot Detection Distance * temperature per species 

```{r}
#M.oxyotus
#TS (20mm)
pMoDD20_nd <- interact_plot(Mo20_DDtype_nd, pred = temp, modx = DDtype, interval = TRUE,
              line.thickness = 2,
              plot.points = TRUE,
              point.alpha = 1,
              point.size = 1.5,
              vary.lty = FALSE,
              int.width = 0.95,x.label = "Temperature (°C)", y.label = "Detection Distance (m)",
              colors = c("gray47","darkolivegreen4"),
              modx.labels = c("Ambient model","Experimental model"))+ 
              theme_apa(legend.font.size = 14,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

pMoDD20_nd <- pMoDD20_nd + xlim(18, 25) + ylim(0.9, 1.5) + theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))



# Definir la ruta y el nombre del archivo
Mo2D_DDtype_nd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mo2D_DDtype_nd.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mo2D_DDtype_nd, plot = pMoDD20_nd, dpi = 300, width = 15, height = 10, units = "cm") 

```

# Myotis pilosatibialis 

```{r}

#TS -20
colnames(GLM_Mk20)

#avrg
avrgDD_Mk20 <- GLM_Mk20[c(1:13,26,66)] # column 66 correspond to avrg DD (theoric values)
names(avrgDD_Mk20)[15]<-paste("DD")
avrgDD_Mk20$DDtype <- "avrgDD"
#realDD2
realDD2_Mk20 <- GLM_Mk20[c(1:13,26,67)]
names(realDD2_Mk20)[15]<-paste("DD") # column 67 correspond to real DD (observed values)
realDD2_Mk20$DDtype <- "realDD2"

DD_Mk20 <- rbind(avrgDD_Mk20,realDD2_Mk20) #bind dataframes
head(DD_Mk20)

#Filter data bellow 1.5 in distance 
filt_DD_Mk20 <- subset(DD_Mk20, distB2Mic >= 1.5)
head(filt_DD_Mk20)
nrow(DD_Mk20)
nrow(filt_DD_Mk20)

#make models for average and observed parameters (non-responsive vs responsive bat)
Mk20_DDtype_nd <- lmer(DD ~ DDtype * temp + (temp|Ind), data=DD_Mk20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))
Mk20_DDtype_wd <- lmer(DD ~ DDtype * temp * distB2Mic + (temp|Ind), data=DD_Mk20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))

#model_nd
coef(Mk20_DDtype_nd)
anova(Mk20_DDtype_nd)
summary(Mk20_DDtype_nd)
#model_wd
coef(Mk20_DDtype_wd)
anova(Mk20_DDtype_wd)
summary(Mk20_DDtype_wd)

#Random slope summary table
Mk20_tDDm_nd = sjPlot:: tab_Model(Mk20_DDtype_nd)
#Random slope summary table
Mk20_tDDm_wf = sjPlot:: tab_model(Mk20_DDtype_wd)

tab_model(Mk20_DDtype_nd, Mk20_DDtype_wd,show.aic = TRUE) #compare models in one single table

#Effect sizes
effectsize(Mk20_DDtype_nd)
effectsize(Mk20_DDtype_wd)

#create table with confidence intervals
ggeffect(Mk20_DDtype_nd, "temp", ci_level = 0.95)
ggpredict(Mk20_DDtype_nd, "temp", ci_level = 0.95)
#create table with confidence intervals
ggeffect(Mk20_DDtype_wd, "temp", ci_level = 0.95)
ggpredict(Mk20_DDtype_wd, "temp", ci_level = 0.95)


#create table with confidence intervals
resultMk20_DDm_nd <- ggpredict(Mk20_DDtype_nd, c("temp","DDtype"))
resultMk20_DDm_nd
#create table with confidence intervals
resultMk20_DDm_wd <- ggpredict(Mk20_DDtype_wd, c("temp","DDtype"))
resultMk20_DDm_wd


```

#Plot Myotis pilosatibialis 

```{r}
# Separate the dataframe into two based on AAtype
DDavrg_Mk <- subset(DD_Mk20, DDtype == "avrgDD")
DDreal_Mk <- subset(DD_Mk20, DDtype == "realDD2")

# Function to generate predictions for grid values
generate_predictions <- function(model, data, temp_seq, dist_seq) {
  grid <- expand.grid(temp = temp_seq, distB2Mic = dist_seq)
  grid$DDtype <- unique(data$DDtype) # Ensure the correct AAtype is used
  grid$Ind <- NA # Placeholder, if required by the model
  
  # Predict using the model and new data
  grid$pred_DD <- predict(model, newdata = grid, re.form = NA)
  return(grid)
}

# Generate temperature and distance sequences
tr_DDreal_Mk <- seq(min(DDreal_Mk$temp), max(DDreal_Mk$temp), length.out = 30)
dr_DDreal_Mk <- seq(min(DDreal_Mk$distB2Mic), max(DDreal_Mk$distB2Mic), length.out = 30)

# Generate predictions for AAFp
gr_DDreal_Mk_wd <- generate_predictions(Mk20_DDtype_wd, DDreal_Mk, tr_DDreal_Mk, dr_DDreal_Mk)

#DDmean

# Generate temperature and distance sequences
tr_DDavrg_Mk <- seq(min(DDavrg_Mk$temp), max(DDavrg_Mk$temp), length.out = 30)
dr_DDavrg_Mk <- seq(min(DDavrg_Mk$distB2Mic), max(DDavrg_Mk$distB2Mic), length.out = 30)

# Generate predictions for AAFp
gr_DDavrg_Mk_wd <- generate_predictions(Mk20_DDtype_wd, DDavrg_Mk, tr_DDavrg_Mk, dr_DDavrg_Mk)

# Plot image with discrete colors
p2Mk_DDreal_wd <- ggplot(gr_DDreal_Mk_wd, aes(x = temp, y = distB2Mic, fill = cut(pred_DD, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "DDreal") +
  scale_fill_manual(values = colors) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold")  # Increase y-axis title size
  )

# Definir la ruta y el nombre del archivo
Mk2D_DDreal_wd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mk2D_DDreal_wd.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mk2D_DDreal_wd, plot = p2Mk_DDreal_wd, dpi = 300, width = 15, height = 10, units = "cm")

p2Mk_DDavrg_wd <- ggplot(gr_DDavrg_Mk_wd, aes(x = temp, y = distB2Mic, fill = cut(pred_DD, breaks = 8))) +
  geom_tile() +
  labs(x = "Temperature (°C)", y = "Distance to Microphone (m)", fill = "DDavrg") +
  scale_fill_manual(values = colors)+
  theme_minimal()+
  theme(
    axis.text.x = element_text(size = 15),  # Increase x-axis text size
    axis.text.y = element_text(size = 15),  # Increase y-axis text size
    axis.title.x = element_text(size = 14,face="bold"), # Increase x-axis title size
    axis.title.y = element_text(size = 14,face="bold")  # Increase y-axis title size
  )

# Definir la ruta y el nombre del archivo
Mk2D_DDmean_wd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mk2D_DDmean_wd.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mk2D_DDmean_wd, plot = p2Mk_DDavrg_wd, dpi = 300, width = 15, height = 10, units = "cm")

```


```{r}
#I use these 3d graphics for legend purpose
# Prepare the data for plotting in persp3D
x_DDavrg_wd <- matrix(gr_DDavrg_Mk_wd$temp, nrow = 30, byrow = TRUE)
y_DDavrg_wd <- matrix(gr_DDavrg_Mk_wd$distB2Mic, nrow = 30, byrow = TRUE)
z_DDavrg_wd <- matrix(gr_DDavrg_Mk_wd$pred_DD, nrow = 30, byrow = TRUE)

png(filename = paste0("F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/NEW/","Mk_DDavrg_wd3d", ".png"), res = 300, width = 1700, height = 1700)
#Plot
persp3D(x_DDavrg_wd, 
        y_DDavrg_wd, 
        z_DDavrg_wd, 
        phi = 404,
        theta = -40 + 360,
        xlab = "Temperature", 
        ylab = "Distance to Mic", 
        zlab = "DDavrg", 
        col = rev(col_palette), 
        border = adjustcolor("black", 0.3),
        bty = "u")

dev.off()

# Prepare the data for plotting in persp3D
x_DDreal_wd <- matrix(gr_DDreal_Mk_wd$temp, nrow = 30, byrow = TRUE)
y_DDreal_wd <- matrix(gr_DDreal_Mk_wd$distB2Mic, nrow = 30, byrow = TRUE)
z_DDreal_wd <- matrix(gr_DDreal_Mk_wd$pred_DD, nrow = 30, byrow = TRUE)

png(filename = paste0("F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/NEW/","Mk_DDreal_wd3d", ".png"), res = 300, width = 1700, height = 1700)
#Plot
persp3D(x_DDreal_wd, 
        y_DDreal_wd, 
        z_DDreal_wd, 
        phi = 404,
        theta = -40 + 360,
        xlab = "Temperature", 
        ylab = "Distance to Mic", 
        zlab = "DDreal", 
        col = rev(col_palette), 
        border = adjustcolor("black", 0.3),
        bty = "u")

dev.off()



```


# Myotis riparius 

```{r}

#TS -20
colnames(GLM_Mr20)

#avrg
avrgDD_Mr20 <- GLM_Mr20[c(1:13,26,66)] # column 66 correspond to avrg DD (theoric values)
names(avrgDD_Mr20)[15]<-paste("DD")
avrgDD_Mr20$DDtype <- "avrgDD"
#realDD2
realDD2_Mr20 <- GLM_Mr20[c(1:13,26,67)]
names(realDD2_Mr20)[15]<-paste("DD") # column 67 correspond to real DD (observed values)
realDD2_Mr20$DDtype <- "realDD2"

DD_Mr20 <- rbind(avrgDD_Mr20,realDD2_Mr20) #bind dataframes
head(DD_Mr20)

#Filter data bellow 1.5 in distance 
filt_DD_Mr20 <- subset(DD_Mr20, distB2Mic >= 1.5)
head(filt_DD_Mr20)
nrow(DD_Mr20)
nrow(filt_DD_Mr20)

#make models for average and observed parameters (non-responsive vs responsive bat)
Mr20_DDtype_nd <- lmer(DD ~ DDtype * temp + (temp|Ind), data=DD_Mr20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))
Mr20_DDtype_wd <- lmer(DD ~ DDtype * temp * distB2Mic + (temp|Ind), data=DD_Mr20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))

#model_nd
coef(Mr20_DDtype_nd)
anova(Mr20_DDtype_nd)
summary(Mr20_DDtype_nd)
#model_wd
coef(Mr20_DDtype_wd)
anova(Mr20_DDtype_wd)
summary(Mr20_DDtype_wd)

#Random slope summary table
Mr20_tDDm_nd = sjPlot:: tab_model(Mr20_DDtype_nd)
#Random slope summary table
Mr20_tDDm_wf = sjPlot:: tab_model(Mr20_DDtype_wd)

tab_model(Mr20_DDtype_nd, Mr20_DDtype_wd,show.aic = TRUE) #compare models in one single table

#Effect sizes
effectsize(Mr20_DDtype_nd)
effectsize(Mr20_DDtype_wd)

#create table with confidence intervals
ggeffect(Mr20_DDtype_nd, "temp", ci_level = 0.95)
ggpredict(Mr20_DDtype_nd, "temp", ci_level = 0.95)
#create table with confidence intervals
ggeffect(Mr20_DDtype_wd, "temp", ci_level = 0.95)
ggpredict(Mr20_DDtype_wd, "temp", ci_level = 0.95)


#create table with confidence intervals
resultMr20_DDm_nd <- ggpredict(Mr20_DDtype_nd, c("temp","DDtype"))
resultMr20_DDm_nd
#create table with confidence intervals
resultMr20_DDm_wd <- ggpredict(Mr20_DDtype_wd, c("temp","DDtype"))
resultMr20_DDm_wd

```

# Plot Detection Distance * temperature per species 

```{r}
#M.riparius
#TS (20mm)
pMrDD20_nd <- interact_plot(Mr20_DDtype_nd, pred = temp, modx = DDtype, interval = TRUE,
              line.thickness = 2,
              plot.points = TRUE,
              point.alpha = 1,
              point.size = 1.5,
              vary.lty = FALSE,
              int.width = 0.95,x.label = "Temperature (°C)", y.label = "Detection Distance (m)",
              colors = c("gray47","coral3"),
              modx.labels = c("Ambient model","Experimental model"))+ 
              theme_apa(legend.font.size = 14,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

pMrDD20_nd <- pMrDD20_nd + xlim(18, 25) + ylim(0.8, 1.6) + theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))



# Definir la ruta y el nombre del archivo
Mr2D_DDtype_nd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mr2D_DDtype_nd.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mr2D_DDtype_nd, plot = pMrDD20_nd, dpi = 300, width = 15, height = 10, units = "cm") 

```

# Myotis group

```{r}

#TS -20
colnames(GLM_Mg20)

#avrg
avrgDD_Mg20 <- GLM_Mg20[c(1:13,26,66)] # column 66 correspond to avrg DD (theoric values)
names(avrgDD_Mg20)[15]<-paste("DD")
avrgDD_Mg20$DDtype <- "avrgDD"
#realDD2
realDD2_Mg20 <- GLM_Mg20[c(1:13,26,67)]
names(realDD2_Mg20)[15]<-paste("DD") # column 67 correspond to real DD (observed values)
realDD2_Mg20$DDtype <- "realDD2"

DD_Mg20 <- rbind(avrgDD_Mg20,realDD2_Mg20) #bind dataframes
head(DD_Mg20)

#Filter data bellow 1.5 in distance 
filt_DD_Mg20 <- subset(DD_Mg20, distB2Mic >= 1.5)
head(filt_DD_Mg20)
nrow(DD_Mg20)
nrow(filt_DD_Mg20)

#make models for average and observed parameters (non-responsive vs responsive bat)
Mg20_DDtype_nd <- lmer(DD ~ DDtype * temp + (temp|Ind), data=DD_Mg20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))
Mg20_DDtype_wd <- lmer(DD ~ DDtype * temp * distB2Mic + (temp|Ind), data=DD_Mg20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))

#model_nd
coef(Mg20_DDtype_nd)
anova(Mg20_DDtype_nd)
summary(Mg20_DDtype_nd)
#model_wd
coef(Mg20_DDtype_wd)
anova(Mg20_DDtype_wd)
summary(Mg20_DDtype_wd)

#Random slope summary table
Mg20_tDDm_nd = sjPlot:: tab_model(Mg20_DDtype_nd)
#Random slope summary table
Mg20_tDDm_wf = sjPlot:: tab_model(Mg20_DDtype_wd)

tab_model(Mg20_DDtype_nd, Mg20_DDtype_wd,show.aic = TRUE) #compare models in one single table

#Effect sizes
effectsize(Mg20_DDtype_nd)
effectsize(Mg20_DDtype_wd)

#create table with confidence intervals
ggeffect(Mg20_DDtype_nd, "temp", ci_level = 0.95)
ggpredict(Mg20_DDtype_nd, "temp", ci_level = 0.95)
#create table with confidence intervals
ggeffect(Mg20_DDtype_wd, "temp", ci_level = 0.95)
ggpredict(Mg20_DDtype_wd, "temp", ci_level = 0.95)


#create table with confidence intervals
resultMg20_DDm_nd <- ggpredict(Mg20_DDtype_nd, c("temp","DDtype"))
resultMg20_DDm_nd
#create table with confidence intervals
resultMg20_DDm_wd <- ggpredict(Mg20_DDtype_wd, c("temp","DDtype"))
resultMg20_DDm_wd

```

# Plot Detection Distance * temperature per species 

```{r}
#M.group
#TS (20mm)
pMgDD20_nd <- interact_plot(Mg20_DDtype_nd, pred = temp, modx = DDtype, interval = TRUE,
              line.thickness = 2,
              plot.points = TRUE,
              point.alpha = 1,
              point.size = 1.5,
              vary.lty = FALSE,
              int.width = 0.95,x.label = "Temperature (°C)", y.label = "Detection Distance (m)",
              colors = c("gray47","darkgoldenrod1"),
              modx.labels = c("Ambient model","Experimental model"))+ 
              theme_apa(legend.font.size = 14,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

pMgDD20_nd <- pMgDD20_nd + xlim(18, 25) + ylim(0.5, 2) + theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))



# Definir la ruta y el nombre del archivo
Mg2D_DDtype_nd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mg2D_DDtype_nd.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mg2D_DDtype_nd, plot = pMgDD20_nd, dpi = 300, width = 15, height = 10, units = "cm") 

```

# Eptesicus brasiliensis

```{r}

#TS -20
colnames(GLM_Eb20)

#avrg
avrgDD_Eb20 <- GLM_Eb20[c(1:13,26,66)] # column 66 correspond to avrg DD (theoric values)
names(avrgDD_Eb20)[15]<-paste("DD")
avrgDD_Eb20$DDtype <- "avrgDD"
#realDD2
realDD2_Eb20 <- GLM_Eb20[c(1:13,26,67)]
names(realDD2_Eb20)[15]<-paste("DD") # column 67 correspond to real DD (observed values)
realDD2_Eb20$DDtype <- "realDD2"

DD_Eb20 <- rbind(avrgDD_Eb20,realDD2_Eb20) #bind dataframes
head(DD_Eb20)

#Filter data bellow 1.5 in distance 
filt_DD_Eb20 <- subset(DD_Eb20, distB2Mic >= 1.5)
head(filt_DD_Eb20)
nrow(DD_Eb20)
nrow(filt_DD_Eb20)

#make models for average and observed parameters (non-responsive vs responsive bat)
Eb20_DDtype_nd <- lmer(DD ~ DDtype * temp + (temp|Ind), data=DD_Eb20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))
Eb20_DDtype_wd <- lmer(DD ~ DDtype * temp * distB2Mic + (temp|Ind), data=DD_Eb20, REML = F,
                    control = lmerControl(optimizer ="Nelder_Mead"))

#model_nd
coef(Eb20_DDtype_nd)
anova(Eb20_DDtype_nd)
summary(Eb20_DDtype_nd)
#model_wd
coef(Eb20_DDtype_wd)
anova(Eb20_DDtype_wd)
summary(Eb20_DDtype_wd)

#Random slope summary table
Eb20_tDDm_nd = sjPlot:: tab_model(Eb20_DDtype_nd)
#Random slope summary table
Eb20_tDDm_wf = sjPlot:: tab_model(Eb20_DDtype_wd)

tab_model(Eb20_DDtype_nd, Eb20_DDtype_wd,show.aic = TRUE) #compare models in one single table

#Effect sizes
effectsize(Eb20_DDtype_nd)
effectsize(Eb20_DDtype_wd)

#create table with confidence intervals
ggeffect(Eb20_DDtype_nd, "temp", ci_level = 0.95)
ggpredict(Eb20_DDtype_nd, "temp", ci_level = 0.95)
#create table with confidence intervals
ggeffect(Eb20_DDtype_wd, "temp", ci_level = 0.95)
ggpredict(Eb20_DDtype_wd, "temp", ci_level = 0.95)


#create table with confidence intervals
resultEb20_DDm_nd <- ggpredict(Eb20_DDtype_nd, c("temp","DDtype"))
resultEb20_DDm_nd
#create table with confidence intervals
resultEb20_DDm_wd <- ggpredict(Eb20_DDtype_wd, c("temp","DDtype"))
resultEb20_DDm_wd

```

# Plot Detection Distance * temperature per species 

```{r}
#E. brasiliensis
#TS (20mm)
pEbDD20_nd <- interact_plot(Eb20_DDtype_nd, pred = temp, modx = DDtype, interval = TRUE,
              line.thickness = 2,
              plot.points = TRUE,
              point.alpha = 1,
              point.size = 1.5,
              vary.lty = FALSE,
              int.width = 0.95,x.label = "Temperature (°C)", y.label = "Detection Distance (m)",
              colors = c("gray47","dodgerblue2"),
              modx.labels = c("Ambient model","Experimental model"))+ 
              theme_apa(legend.font.size = 14,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

pEbDD20_nd <- pEbDD20_nd + xlim(18, 25) + ylim(0.8, 1.6) + theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
        plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))



# Definir la ruta y el nombre del archivo
Eb2D_DDtype_nd <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Eb2D_DDtype_nd.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Eb2D_DDtype_nd, plot = pEbDD20_nd, dpi = 300, width = 15, height = 10, units = "cm") 

```

#Read data sets - Atmospheric Attenuation for fixed values of Relative Humidity (RH)
# RH = 100

```{r}

AA_RH100= read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_processed_data/AA_RH100.csv", header = T, sep = ",")
colnames(AA_RH100)
AA_RH100 <- as.data.frame(AA_RH100[,-1])
str(AA_RH100)


Ind = as.data.frame(sprintf("%03d", AA_RH100$Ind))
names(Ind)[1]<-paste("Ind")
AA_RH100 <- cbind(AA_RH100, Ind)
AA_RH100 <- AA_RH100[, c(1:2,64,4:63)]
AA_RH100[, 'Ind'] <- as.factor(AA_RH100[,'Ind'])

i <- c(36:38)#create the i vector with the columns that I need to be numeric
#convert character to numeric from column 10 to 142
AA_RH100[ , i] <- apply(AA_RH100[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10:11,63)#create the i vector with the columns that I need to be as.character

AA_RH100[ , i] <- apply(AA_RH100[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))





```

# RH = 75

```{r}

AA_RH75= read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_processed_data/AA_RH75.csv", header = T, sep = ",")
colnames(AA_RH75)
AA_RH75 <- as.data.frame(AA_RH75[,-1])
str(AA_RH75)


Ind = as.data.frame(sprintf("%03d", AA_RH75$Ind))
names(Ind)[1]<-paste("Ind")
AA_RH75 <- cbind(AA_RH75, Ind)
AA_RH75 <- AA_RH75[, c(1:2,64,4:63)]
AA_RH75[, 'Ind'] <- as.factor(AA_RH75[,'Ind'])

i <- c(36:38)#create the i vector with the columns that I need to be numeric
#convert character to numeric from column 10 to 142
AA_RH75[ , i] <- apply(AA_RH75[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10:11,63)#create the i vector with the columns that I need to be as.character

AA_RH75[ , i] <- apply(AA_RH75[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))


```

# RH = 50

```{r}

AA_RH50= read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_processed_data/AA_RH50.csv", header = T, sep = ",")
colnames(AA_RH50)
AA_RH50 <- as.data.frame(AA_RH50[,-1])
str(AA_RH50)


Ind = as.data.frame(sprintf("%03d", AA_RH50$Ind))
names(Ind)[1]<-paste("Ind")
AA_RH50 <- cbind(AA_RH50, Ind)
AA_RH50 <- AA_RH50[, c(1:2,64,4:63)]
AA_RH50[, 'Ind'] <- as.factor(AA_RH50[,'Ind'])

i <- c(36:38)#create the i vector with the columns that I need to be numeric
#convert character to numeric from column 10 to 142
AA_RH50[ , i] <- apply(AA_RH50[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10:11,63)#create the i vector with the columns that I need to be as.character

AA_RH50[ , i] <- apply(AA_RH50[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))

```

#Separate datasets per species

```{r}
#RH100
RH100_Mo <- AA_RH100[ which(AA_RH100$GS=="M.oxyotus"),]
RH100_Mk <- AA_RH100[ which(AA_RH100$GS=="M.keaysi"),]
RH100_Mr <- AA_RH100[ which(AA_RH100$GS=="M.riparius"),]
RH100_Mg <- AA_RH100[ which(AA_RH100$GS=="M.group"),]
RH100_Eb <- AA_RH100[ which(AA_RH100$GS=="E.brasiliensis"),]

#RH75
RH75_Mo <- AA_RH75[ which(AA_RH75$GS=="M.oxyotus"),]
RH75_Mk <- AA_RH75[ which(AA_RH75$GS=="M.keaysi"),]
RH75_Mr <- AA_RH75[ which(AA_RH75$GS=="M.riparius"),]
RH75_Mg <- AA_RH75[ which(AA_RH75$GS=="M.group"),]
RH75_Eb <- AA_RH75[ which(AA_RH75$GS=="E.brasiliensis"),]

#RH50
RH50_Mo <- AA_RH50[ which(AA_RH50$GS=="M.oxyotus"),]
RH50_Mk <- AA_RH50[ which(AA_RH50$GS=="M.keaysi"),]
RH50_Mr <- AA_RH50[ which(AA_RH50$GS=="M.riparius"),]
RH50_Mg <- AA_RH50[ which(AA_RH50$GS=="M.group"),]
RH50_Eb <- AA_RH50[ which(AA_RH50$GS=="E.brasiliensis"),]

#Bind rows for the three values of RH per species 

AA_RHfix_Mo <- rbind(RH100_Mo,RH75_Mo,RH50_Mo) #bind dataframes
AA_RHfix_Mk <- rbind(RH100_Mk,RH75_Mk,RH50_Mk) #bind dataframes
AA_RHfix_Mr <- rbind(RH100_Mr,RH75_Mr,RH50_Mr) #bind dataframes
AA_RHfix_Mg <- rbind(RH100_Mg,RH75_Mg,RH50_Mg) #bind dataframes
AA_RHfix_Eb <- rbind(RH100_Eb,RH75_Eb,RH50_Eb) #bind dataframes



colnames(AA_RHfix_Mo)
summary_RHfixMo <- AA_RHfix_Mo %>%
  group_by(Exp,RHfix) %>%
  summarise(
    minAA = max(AAmeanFp),
    maxAA = min(AAmeanFp),
    meanDD = mean(AAmeanFp),
    sdAA = sd(AAmeanFp),
    )

```

#Make models of Atmospheric Attenuation for fixed values of relative humidity
#M.oxyotus

```{r}
colnames(AA_RHfix_Mo)
AAmeanRHfix_Mo <- AA_RHfix_Mo[c(1:13,60,63)] # column 60 is AA mean (AA with constant values of PF)

#make interaction model
AAmRH_Mo <- lmer(AAmeanFp ~ RHfix * T + (1|Ind), data = AAmeanRHfix_Mo, REML = FALSE)

coef(AAmRH_Mo)
summary(AAmRH_Mo)
anova(AAmRH_Mo)

AAtRH_Mo = sjPlot:: tab_model(AAmRH_Mo)
AAtRH_Mo

# Estimate slopes for each level of RHfix
Mo_slopes <- emtrends(AAmRH_Mo, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
Mo_slopes_p <- summary(Mo_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(Mo_slopes_p)

#create table with confidence intervals
resultAAmRH_Mo <- ggpredict(AAmRH_Mo, c("T","RHfix"))
resultAAmRH_Mo


Mo_p_RHfix <- interact_plot(AAmRH_Mo, pred = T, modx = RHfix,interval = TRUE,int.width = 0.6,
              vary.lty = FALSE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 20,
              y.font.size = 20,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mo_p_RHfix <- Mo_p_RHfix + xlim(18, 25) +  
  scale_y_reverse(limits = c(-1.9, -3.5)) +  # ⬅️ Define los límites e invierte el eje
  theme(
    axis.text.x = element_text(size = 15),  
    axis.text.y = element_text(size = 15),  
    axis.title.x = element_text(size = 14, face = "bold"),  
    axis.title.y = element_text(size = 14, face = "bold")  
  )



# Definir la ruta y el nombre del archivo
Mo_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mo_p_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mo_RHfix, plot = Mo_p_RHfix, dpi = 300, width = 15, height = 10, units = "cm")
```

#M.pilosatibialis

```{r}

colnames(AAmeanRHfix_Mk)
colnames(AA_RHfix_Mk)

AAmeanRHfix_Mk <- AA_RHfix_Mk[c(1:13,60,63)] # column 60 is AA mean (AA with constant values of PF) 


#make interaction model
AAmRH_Mk <- lmer(AAmeanFp ~ RHfix * T + (T|Ind), data=AAmeanRHfix_Mk, REML = F)
coef(AAmRH_Mk)
summary(AAmRH_Mk)
plot(AAmRH_Mk)

AAtRH_Mk = sjPlot:: tab_model(AAmRH_Mk)
AAtRH_Mk

####compare slopes 
# Estimate slopes for each level of RHfix
Mk_slopes <- emtrends(AAmRH_Mk, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
Mk_slopes_p <- summary(Mk_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(Mk_slopes_p)

#create table with confidence intervals
resultAAmRH_Mk <- ggpredict(AAmRH_Mk, c("T","RHfix"))
resultAAmRH_Mk

Mk_p_RHfix <- interact_plot(AAmRH_Mk, pred = T, modx = RHfix,interval = TRUE,int.width = 0.95,
              vary.lty = FALSE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 20,
              y.font.size = 20,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mk_p_RHfix <- Mk_p_RHfix + 
  xlim(18, 25) +  
  scale_y_reverse(limits = c(-2, -3.5)) +  # ⬅️ Define los límites e invierte el eje
  theme(
    axis.text.x = element_text(size = 15),  
    axis.text.y = element_text(size = 15),  
    axis.title.x = element_text(size = 14, face = "bold"),  
    axis.title.y = element_text(size = 14, face = "bold")  
  )


# Definir la ruta y el nombre del archivo
Mk_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mk_p_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mk_RHfix, plot = Mk_p_RHfix, dpi = 300, width = 15, height = 10, units = "cm")

```

#M.riparius

```{r}
colnames(AA_RHfix_Mr)
AAmeanRHfix_Mr <- AA_RHfix_Mr[c(1:13,60,63)] # column 60 is AA mean (AA with constant values of PF)


#make interaction model
AAmRH_Mr <- lmer(AAmeanFp ~ RHfix * T + (T|Ind), data=AAmeanRHfix_Mr, REML = F)
coef(AAmRH_Mr)
summary(AAmRH_Mr)
plot(AAmRH_Mr)

AAtRH_Mr = sjPlot:: tab_model(AAmRH_Mr)
AAtRH_Mr

#create table with confidence intervals
resultAAmRH_Mr <- ggpredict(AAmRH_Mr, c("T","RHfix"))
resultAAmRH_Mr

#Compare slopes
# Estimate slopes for each level of RHfix
Mr_slopes <- emtrends(AAmRH_Mr, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
Mr_slopes_p <- summary(Mr_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(Mr_slopes_p)

#create table with confidence intervals
resultAAmRH_Mr <- ggpredict(AAmRH_Mr, c("T","RHfix"))
resultAAmRH_Mr

Mr_p_RHfix <- interact_plot(AAmRH_Mr, pred = T, modx = RHfix,interval = TRUE,int.width = 0.95,
              vary.lty = FALSE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 20,
              y.font.size = 20,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mr_p_RHfix <- Mr_p_RHfix + xlim(18, 25) +  
  scale_y_reverse(limits = c(-2, -3.5)) +  # ⬅️ Define los límites e invierte el eje
  theme(
    axis.text.x = element_text(size = 15),  
    axis.text.y = element_text(size = 15),  
    axis.title.x = element_text(size = 14, face = "bold"),  
    axis.title.y = element_text(size = 14, face = "bold")  
  )

# Define route and file name
Mr_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mr_p_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mr_RHfix, plot = Mr_p_RHfix, dpi = 300, width = 15, height = 10, units = "cm")
```

#M.nigricans/elegans

```{r}

colnames(AA_RHfix_Mg)

AAmeanRHfix_Mg <- AA_RHfix_Mg[c(1:13,60,63)] # column 60 is AA mean (AA with constant values of PF)


#make interaction model
AAmRH_Mg <- lmer(AAmeanFp ~ RHfix * T + (T|Ind), data=AAmeanRHfix_Mg, REML = F)
AAm2RH_Mg <- lmer(AAFp ~ RHfix * T + (T|Ind), data=AAFpRHfix_Mg, REML = F)
coef(AAmRH_Mg)
summary(AAmRH_Mg)
plot(AAmRH_Mg)

#create table with confidence intervals
resultAAmRH_Mg <- ggpredict(AAmRH_Mg, c("T","RHfix"))
resultAAmRH_Mg


AAtRH_Mg = sjPlot:: tab_model(AAmRH_Mg)
AAtRH_Mg

#Compare slopes
# Estimate slopes for each level of RHfix
Mg_slopes <- emtrends(AAmRH_Mg, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
Mg_slopes_p <- summary(Mg_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(Mg_slopes_p)

resultAAmRH_Mg <- ggpredict(AAmRH_Mg, c("T","RHfix"))
resultAAmRH_Mg

Mg_p_RHfix <- interact_plot(AAmRH_Mg, pred = T, modx = RHfix,interval = TRUE,int.width = 0.95,
              vary.lty = FALSE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 20,
              y.font.size = 20,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mg_p_RHfix <- Mg_p_RHfix + xlim(18, 25) +  
  scale_y_reverse(limits = c(-2, -3.5)) +  # ⬅️ Define los límites e invierte el eje
  theme(
    axis.text.x = element_text(size = 15),  
    axis.text.y = element_text(size = 15),  
    axis.title.x = element_text(size = 14, face = "bold"),  
    axis.title.y = element_text(size = 14, face = "bold")  
  )



# Definir la ruta y el nombre del archivo
Mg_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Mg_p_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Mg_RHfix, plot = Mg_p_RHfix, dpi = 300, width = 15, height = 10, units = "cm")

```

#E.brasiliensis

```{r}

colnames(AA_RHfix_Eb)
AAmeanRHfix_Eb <- AA_RHfix_Eb[c(1:13,60,63)] # column 60 is AAmean (AA with constant values of PF)


#make interaction model
AAmRH_Eb <- lmer(AAmeanFp ~ RHfix * T + (T|Ind), data=AAmeanRHfix_Eb, REML = F)
coef(AAmRH_Eb)
summary(AAmRH_Eb)
plot(AAmRH_Eb)

#create table with confidence intervals
resultAAmRH_Eb <- ggpredict(AAmRH_Eb, c("T","RHfix"))
resultAAmRH_Eb
plot(resultAAmRH_Eb)

AAtRH_Eb = sjPlot:: tab_model(AAmRH_Eb)
AAtRH_Eb

#Compare slopes
# Estimate slopes for each level of RHfix
Eb_slopes <- emtrends(AAmRH_Eb, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
Eb_slopes_p <- summary(Eb_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(Eb_slopes_p)

resultAAmRH_Eb <- ggpredict(AAmRH_Eb, c("T","RHfix"))
resultAAmRH_Eb

Eb_p_RHfix <- interact_plot(AAmRH_Eb, pred = T, modx = RHfix,interval = TRUE,int.width = 0.7,
              vary.lty = FALSE,
              x.label = "Temperature (°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 20,
              y.font.size = 20,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Eb_p_RHfix <- Eb_p_RHfix + xlim(18, 25) +  
  scale_y_reverse(limits = c(-2, -3.5)) +  # ⬅️ Define los límites e invierte el eje
  theme(
    axis.text.x = element_text(size = 15),  
    axis.text.y = element_text(size = 15),  
    axis.title.x = element_text(size = 14, face = "bold"),  
    axis.title.y = element_text(size = 14, face = "bold")  
  )



# Definir la ruta y el nombre del archivo
Eb_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/correct/Eb_p_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = Eb_RHfix, plot = Eb_p_RHfix, dpi = 300, width = 15, height = 10, units = "cm")



```


#Read data sets with Detection Distance
#Graph detection distance - temperature for fixed values of Relative Humidity (RH)
# RH = 100

```{r}


AADD_RH100 <- read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_processed_data/AA_DD20_RH100_thrDur1.csv", header = T, sep = ",")
colnames(AADD_RH100)
AADD_RH100 <- as.data.frame(AADD_RH100[,-c(1)])
str(AADD_RH100)
head(AADD_RH100)

Ind = as.data.frame(sprintf("%03d", AADD_RH100$Ind))
names(Ind)[1]<-paste("Ind")
AADD_RH100 <- cbind(AADD_RH100, Ind)
AADD_RH100 <- AADD_RH100[, c(1:2,72,4:71)]
AADD_RH100[, 'Ind'] <- as.factor(AADD_RH100[,'Ind'])

i <- c(36:38)#create the i vector with the columns that I need to be numeric
#convert character to numeric from column 10 to 142
AADD_RH100[ , i] <- apply(AADD_RH100[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10:11,63,71)#create the i vector with the columns that I need to be as.character

AADD_RH100[ , i] <- apply(AADD_RH100[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))

head(AADD_RH100)

```

# RH = 75

```{r}

AADD_RH75= read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_processed_data/AA_DD20_RH75_thrDur1.csv", header = T, sep = ",")
colnames(AADD_RH75)
AADD_RH75 <- as.data.frame(AADD_RH75[,-1])
str(AADD_RH75)


Ind = as.data.frame(sprintf("%03d", AADD_RH75$Ind))
names(Ind)[1]<-paste("Ind")
AADD_RH75 <- cbind(AADD_RH75, Ind)
AADD_RH75 <- AADD_RH75[, c(1:2,72,4:71)]
AADD_RH75[, 'Ind'] <- as.factor(AADD_RH75[,'Ind'])

i <- c(36:38)#create the i vector with the columns that I need to be numeric
#convert character to numeric from column 10 to 142
AADD_RH75[ , i] <- apply(AADD_RH75[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10:11,63,71)#create the i vector with the columns that I need to be as.character

AADD_RH75[ , i] <- apply(AADD_RH75[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))

head(AADD_RH75)

```

# RH = 50

```{r}

AADD_RH50 <- read.csv(file = "F:/PhD_Project/Sensory_Ecology/R/R_processed_data/AA_DD20_RH50_thrDur1.csv", header = T, sep = ",")
colnames(AADD_RH50)
AADD_RH50 <- as.data.frame(AADD_RH50[,-1])
str(AADD_RH50)


Ind = as.data.frame(sprintf("%03d", AADD_RH50$Ind))
names(Ind)[1]<-paste("Ind")
AADD_RH50 <- cbind(AADD_RH50, Ind)
AADD_RH50 <- AADD_RH50[, c(1:2,72,4:71)]
AADD_RH50[, 'Ind'] <- as.factor(AADD_RH50[,'Ind'])

i <- c(36:38)#create the i vector with the columns that I need to be numeric
#convert character to numeric from column 10 to 142
AADD_RH50[ , i] <- apply(AADD_RH50[ , i], 2,            # Specify own function within apply
                    function(x) as.numeric(as.integer(x)))

i <- c(4:6,10:11,63,71)#create the i vector with the columns that I need to be as.character

AADD_RH50[ , i] <- apply(AADD_RH50[ , i], 2,            # Specify own function within apply
                    function(x) as.character(as.integer(x)))

head(AADD_RH50)

```


```{r}

#rename columns in AADD_RH100,AADD_RH75 y AADD_RH50 for rbind

colnames(AADD_RH100)
colnames(AADD_RH100)[colnames(AADD_RH100) == "avrgDD_RH100"] <- "avrgDD"
colnames(AADD_RH100)[colnames(AADD_RH100) == "realDD2_RH100"] <- "realDD2"
colnames(AADD_RH100)[colnames(AADD_RH100) == "realDD_RH100"] <- "realDD"
colnames(AADD_RH100)[colnames(AADD_RH100) == "frqDD_RH100"] <- "frqDD"
colnames(AADD_RH100)[colnames(AADD_RH100) == "rmsDD_RH100"] <- "rmsDD"
colnames(AADD_RH100)[colnames(AADD_RH100) == "durDD_RH100"] <- "durDD"

colnames(AADD_RH75)
colnames(AADD_RH75)[colnames(AADD_RH75) == "avrgDD_RH75"] <- "avrgDD"
colnames(AADD_RH75)[colnames(AADD_RH75) == "realDD2_RH75"] <- "realDD2"
colnames(AADD_RH75)[colnames(AADD_RH75) == "realDD_RH75"] <- "realDD"
colnames(AADD_RH75)[colnames(AADD_RH75) == "frqDD_RH75"] <- "frqDD"
colnames(AADD_RH75)[colnames(AADD_RH75) == "rmsDD_RH75"] <- "rmsDD"
colnames(AADD_RH75)[colnames(AADD_RH75) == "durDD_RH75"] <- "durDD"

colnames(AADD_RH50)
colnames(AADD_RH50)[colnames(AADD_RH50) == "avrgDD_RH50"] <- "avrgDD"
colnames(AADD_RH50)[colnames(AADD_RH50) == "realDD2_RH50"] <- "realDD2"
colnames(AADD_RH50)[colnames(AADD_RH50) == "realDD_RH50"] <- "realDD"
colnames(AADD_RH50)[colnames(AADD_RH50) == "frqDD_RH50"] <- "frqDD"
colnames(AADD_RH50)[colnames(AADD_RH50) == "rmsDD_RH50"] <- "rmsDD"
colnames(AADD_RH50)[colnames(AADD_RH50) == "durDD_RH50"] <- "durDD"

#RH100
AADDRH100_Mo <- AADD_RH100[ which(AADD_RH100$GS=="M.oxyotus"),]
AADDRH100_Mk <- AADD_RH100[ which(AADD_RH100$GS=="M.keaysi"),]
AADDRH100_Mr <- AADD_RH100[ which(AADD_RH100$GS=="M.riparius"),]
AADDRH100_Mg <- AADD_RH100[ which(AADD_RH100$GS=="M.group"),]
AADDRH100_Eb <- AADD_RH100[ which(AADD_RH100$GS=="E.brasiliensis"),]

#RH75
AADDRH75_Mo <- AADD_RH75[ which(AADD_RH75$GS=="M.oxyotus"),]
AADDRH75_Mk <- AADD_RH75[ which(AADD_RH75$GS=="M.keaysi"),]
AADDRH75_Mr <- AADD_RH75[ which(AADD_RH75$GS=="M.riparius"),]
AADDRH75_Mg <- AADD_RH75[ which(AADD_RH75$GS=="M.group"),]
AADDRH75_Eb <- AADD_RH75[ which(AADD_RH75$GS=="E.brasiliensis"),]

#RH50
AADDRH50_Mo <- AADD_RH50[ which(AADD_RH50$GS=="M.oxyotus"),]
AADDRH50_Mk <- AADD_RH50[ which(AADD_RH50$GS=="M.keaysi"),]
AADDRH50_Mr <- AADD_RH50[ which(AADD_RH50$GS=="M.riparius"),]
AADDRH50_Mg <- AADD_RH50[ which(AADD_RH50$GS=="M.group"),]
AADDRH50_Eb <- AADD_RH50[ which(AADD_RH50$GS=="E.brasiliensis"),]

AADD_RHfix_Mo <- rbind(AADDRH100_Mo,AADDRH75_Mo,AADDRH50_Mo) #bind dataframes
AADD_RHfix_Mk <- rbind(AADDRH100_Mk,AADDRH75_Mk,AADDRH50_Mk) #bind dataframes
AADD_RHfix_Mr <- rbind(AADDRH100_Mr,AADDRH75_Mr,AADDRH50_Mr) #bind dataframes
AADD_RHfix_Mg <- rbind(AADDRH100_Mg,AADDRH75_Mg,AADDRH50_Mg) #bind dataframes
AADD_RHfix_Eb <- rbind(AADDRH100_Eb,AADDRH75_Eb,AADDRH50_Eb) #bind dataframes

```

# Models and plot with RH fix for Detection Ranges
# Myotis oxyotus

```{r}


#Detection Ranges
colnames(AADD_RHfix_Mo)
DDmeanRHfix_Mo <- AADD_RHfix_Mo[c(1:13,65,63)] # column 63 & 65 are fixRH and avrgDD (DD w/ observed values) 

#make interaction model
DDmRH_Mo <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mo, REML = F)

coef(DDmRH_Mo)
summary(DDmRH_Mo)
plot(DDmRH_Mo)

DDtRH_Mo = sjPlot:: tab_model(DDmRH_Mo)
DDtRH_Mo

# Estimate slopes for each level of RHfix
MoDD_slopes <- emtrends(DDmRH_Mo, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
MoDD_slopes_p <- summary(MoDD_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(MoDD_slopes_p)


#create table with confidence intervals
resultDDmRH_Mo <- ggpredict(DDmRH_Mo, c("T","RHfix"))
resultDDmRH_Mo

Mo_DDp_RHfix <- interact_plot(DDmRH_Mo, pred = T, modx = RHfix,interval = TRUE,int.width = 0.7,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

Mo_DDp_RHfix <- Mo_DDp_RHfix + xlim(18, 25) + ylim(1, 1.6)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMo_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMo_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMo_RHfix, plot = Mo_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")


```

# Myotis pilosatibialis

```{r}


#Detection Ranges
colnames(AADD_RHfix_Mk)
DDmeanRHfix_Mk <- AADD_RHfix_Mk[c(1:13,65,63)] # column 63 & 65 are fixRH and avrgDD (DD w/ observed values) 

#make interaction Model
DDmRH_Mk <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mk, REML = F)

coef(DDmRH_Mk)
summary(DDmRH_Mk)
plot(DDmRH_Mk)

DDtRH_Mk = sjPlot:: tab_model(DDmRH_Mk)
DDtRH_Mk

# Estimate slopes for each level of RHfix
MkDD_slopes <- emtrends(DDmRH_Mk, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
MkDD_slopes_p <- summary(MkDD_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(MkDD_slopes_p)

#create table with confidence intervals
resultDDmRH_Mk <- ggpredict(DDmRH_Mk, c("T","RHfix"))
resultDDmRH_Mk

Mk_DDp_RHfix <- interact_plot(DDmRH_Mk, pred = T, modx = RHfix,interval = TRUE,int.width = 0.9,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)


Mk_DDp_RHfix <- Mk_DDp_RHfix + xlim(18, 25) + ylim(1.1, 1.6)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMk_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMk_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMk_RHfix, plot = Mk_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")


```


# Myotis riparius

```{r}


#Detection Ranges
colnames(AADD_RHfix_Mr)
DDmeanRHfix_Mr <- AADD_RHfix_Mr[c(1:13,65,63)] # column 63 & 65 are fixRH and avrgDD (DD w/ observed values) 

#make interaction Model
DDmRH_Mr <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mr, REML = F)

coef(DDmRH_Mr)
summary(DDmRH_Mr)
plot(DDmRH_Mr)

DDtRH_Mr = sjPlot:: tab_model(DDmRH_Mr)
DDtRH_Mr

# Estimate slopes for each level of RHfix
MrDD_slopes <- emtrends(DDmRH_Mr, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
MrDD_slopes_p <- summary(MrDD_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(MrDD_slopes_p)

#create table with confidence intervals
resultDDmRH_Mr <- ggpredict(DDmRH_Mr, c("T","RHfix"))
resultDDmRH_Mr

Mr_DDp_RHfix <- interact_plot(DDmRH_Mr, pred = T, modx = RHfix,interval = TRUE,int.width = 0.9,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)


Mr_DDp_RHfix <- Mr_DDp_RHfix + xlim(18, 25) + ylim(1.1, 1.6)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMr_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMr_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMr_RHfix, plot = Mr_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")


```

# Myotis nigricans/elegans

```{r}


#Detection Ranges
colnames(AADD_RHfix_Mg)
DDmeanRHfix_Mg <- AADD_RHfix_Mg[c(1:13,65,63)] # column 63 & 65 are fixRH and avrgDD (DD w/ observed values) 

#make interaction Model
DDmRH_Mg <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mg, REML = F)

coef(DDmRH_Mg)
summary(DDmRH_Mg)
plot(DDmRH_Mg)

DDtRH_Mg = sjPlot:: tab_model(DDmRH_Mg)
DDtRH_Mg

# Estimate slopes for each level of RHfix
MgDD_slopes <- emtrends(DDmRH_Mg, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
MgDD_slopes_p <- summary(MgDD_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(MgDD_slopes_p)

#create table with confidence intervals
resultDDmRH_Mg <- ggpredict(DDmRH_Mg, c("T","RHfix"))
resultDDmRH_Mg

Mg_DDp_RHfix <- interact_plot(DDmRH_Mg, pred = T, modx = RHfix,interval = TRUE,int.width = 0.7,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)


Mg_DDp_RHfix <- Mg_DDp_RHfix + xlim(18, 25) + ylim(1.1, 1.6)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMg_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMg_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMg_RHfix, plot = Mg_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")


```

# Eptesicus brasiliensis

```{r}


#Detection Ranges
colnames(AADD_RHfix_Eb)
DDmeanRHfix_Eb <- AADD_RHfix_Eb[c(1:13,65,63)] # column 63 & 65 are fixRH and avrgDD (DD w/ observed values) 

#make interaction Model
DDmRH_Eb <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Eb, REML = F)

coef(DDmRH_Eb)
summary(DDmRH_Eb)
plot(DDmRH_Eb)

DDtRH_Eb = sjPlot:: tab_model(DDmRH_Eb)
DDtRH_Eb

# Estimate slopes for each level of RHfix
EbDD_slopes <- emtrends(DDmRH_Eb, specs = "RHfix", var = "T")

# Add p-values for each RHfix slope
EbDD_slopes_p <- summary(EbDD_slopes, infer = c(TRUE, TRUE))

# Print the slopes with p-values
print(EbDD_slopes_p)
print(MkDD_slopes_p)

#create table with confidence intervals
resultDDmRH_Eb <- ggpredict(DDmRH_Eb, c("T","RHfix"))
resultDDmRH_Eb

Eb_DDp_RHfix <- interact_plot(DDmRH_Eb, pred = T, modx = RHfix,interval = TRUE,int.width = 0.7,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)


Eb_DDp_RHfix <- Eb_DDp_RHfix + xlim(18, 25) + ylim(1.1, 1.6)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDEb_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDEb_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDEb_RHfix, plot = Eb_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")


```



#####x
#M.oxyotus
```{r}


#Atmospheric Attenuation
colnames(AADD_RHfix_Mo)
AAmeanRHfix_Mo <- AADD_RHfix_Mo[c(1:13,60,63)] # column 60 is AAFp (AA assuming no change in Peak Frequency)

colnames(AAmeanRHfix_Mo)

#make interaction model
AAmRH_Mo <- lmer(AAmeanFp ~ RHfix * T + (1|Ind), data = AAmeanRHfix_Mo, REML = F)

coef(AAmRH_Mo)
summary(AAmRH_Mo)
anova(AAmRH_Mo)
plot(AAmRH_Mo)

AAtRH_Mo = sjPlot:: tab_model(AAmRH_Mo)
AAtRH_Mo


#create table with confidence intervals
resultAAmRH_Mo <- ggpredict(AAmRH_Mo, c("T","RHfix"))
resultAAmRH_Mo

Mo_AAp_RHfix <- interact_plot(AAmRH_Mo, pred = T, modx = RHfix,interval = TRUE,int.width = 0.6,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mo_AAp_RHfix <- Mo_AAp_RHfix + xlim(18, 25) +  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()



# Definir la ruta y el nombre del archivo
AAMo_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/AAMo_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = AAMo_RHfix, plot = Mo_AAp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")


#M.oxyotus
#Detection Ranges
colnames(AADD_RHfix_Mo)
DDmeanRHfix_Mo <- AADD_RHfix_Mo[c(1:13,65,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(DDmeanRHfix_Mo)

#make interaction model
DDmRH_Mo <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mo, REML = F)

coef(DDmRH_Mo)
summary(DDmRH_Mo)
plot(DDmRH_Mo)

DDtRH_Mo = sjPlot:: tab_model(DDmRH_Mo)
DDtRH_Mo


#create table with confidence intervals
resultDDmRH_Mo <- ggpredict(DDmRH_Mo, c("T","RHfix"))
resultDDmRH_Mo

Mo_DDp_RHfix <- interact_plot(DDmRH_Mo, pred = T, modx = RHfix,interval = TRUE,int.width = 0.5,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mo_DDp_RHfix <- Mo_DDp_RHfix + xlim(18, 25) +  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMo_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMo_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMo_RHfix, plot = Mo_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")

```


#M.pilosatibialis
```{r}


#Atmospheric Attenuation
colnames(AADD_RHfix_Mk)
AAmeanRHfix_Mk <- AADD_RHfix_Mk[c(1:13,60,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(AAmeanRHfix_Mk)

#make interaction model
AAmRH_Mk <- lmer(AAmeanFp ~ RHfix * T + (1|Ind), data = AAmeanRHfix_Mk, REML = F)

coef(AAmRH_Mk)
summary(AAmRH_Mk)
anova(AAmRH_Mk)
plot(AAmRH_Mk)

AAtRH_Mk = sjPlot:: tab_model(AAmRH_Mk)
AAtRH_Mk

#create table with confidence intervals
resultAAmRH_Mk <- ggpredict(AAmRH_Mk, c("T","RHfix"))
resultAAmRH_Mk

Mk_AAp_RHfix <- interact_plot(AAmRH_Mk, pred = T, modx = RHfix,interval = TRUE,int.width = 0.95,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mk_AAp_RHfix <- Mk_AAp_RHfix + xlim(18, 25) +  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()



# Definir la ruta y el nombre del archivo
AAMk_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/AAMk_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = AAMk_RHfix, plot = Mk_AAp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")



#Detection Ranges
colnames(AADD_RHfix_Mk)
DDmeanRHfix_Mk <- AADD_RHfix_Mk[c(1:13,65,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(DDmeanRHfix_Mk)

#make interaction model
DDmRH_Mk <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mk, REML = F)

coef(DDmRH_Mk)
summary(DDmRH_Mk)
plot(DDmRH_Mk)

DDtRH_Mk = sjPlot:: tab_model(DDmRH_Mk)
DDtRH_Mk


#create table with confidence intervals
resultDDmRH_Mk <- ggpredict(DDmRH_Mk, c("T","RHfix"))
resultDDmRH_Mk

Mk_DDp_RHfix <- interact_plot(DDmRH_Mk, pred = T, modx = RHfix,interval = TRUE,int.width = 0.7,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mk_DDp_RHfix <- Mk_DDp_RHfix + xlim(18, 25) + ylim(1.3, 1.6)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMk_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMk_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMk_RHfix, plot = Mk_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")

```


#M.riparius
```{r}

#Atmospheric Attenuation
colnames(AADD_RHfix_Mr)
AAmeanRHfix_Mr <- AADD_RHfix_Mr[c(1:13,60,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(AAmeanRHfix_Mr)

#make interaction model
AAmRH_Mr <- lmer(AAmeanFp ~ RHfix * T + (1|Ind), data = AAmeanRHfix_Mr, REML = F)

coef(AAmRH_Mr)
summary(AAmRH_Mr)
anova(AAmRH_Mr)
plot(AAmRH_Mr)

AAtRH_Mr = sjPlot:: tab_model(AAmRH_Mr)
AAtRH_Mr

#create table with confidence intervals
resultAAmRH_Mr <- ggpredict(AAmRH_Mr, c("T","RHfix"))
resultAAmRH_Mr

Mr_AAp_RHfix <- interact_plot(AAmRH_Mr, pred = T, modx = RHfix,interval = TRUE,int.width = 0.95,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mr_AAp_RHfix <- Mr_AAp_RHfix + xlim(18, 25) +  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()



# Definir la ruta y el nombre del archivo
AAMr_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/AAMr_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = AAMr_RHfix, plot = Mr_AAp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")



#Detection Distance
colnames(AADD_RHfix_Mr)
DDmeanRHfix_Mr <- AADD_RHfix_Mr[c(1:13,65,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(DDmeanRHfix_Mr)

#make interaction model
DDmRH_Mr <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mr, REML = F)

coef(DDmRH_Mr)
summary(DDmRH_Mr)
plot(DDmRH_Mr)

DDtRH_Mr = sjPlot:: tab_model(DDmRH_Mr)
DDtRH_Mr


#create table with confidence intervals
resultDDmRH_Mr <- ggpredict(DDmRH_Mr, c("T","RHfix"))
resultDDmRH_Mr

Mr_DDp_RHfix <- interact_plot(DDmRH_Mr, pred = T, modx = RHfix,interval = TRUE,int.width = 0.7,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mr_DDp_RHfix <- Mr_DDp_RHfix + xlim(18, 25) + ylim(1.2, 1.5) + theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMr_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMr_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMr_RHfix, plot = Mr_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")

```


#M.nigricans/elegans

```{r}

#Atmospheric Attenuation
colnames(AADD_RHfix_Mg)
AAmeanRHfix_Mg <- AADD_RHfix_Mg[c(1:13,60,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(AAmeanRHfix_Mg)

#make interaction model
AAmRH_Mg <- lmer(AAmeanFp ~ RHfix * T + (1|Ind), data = AAmeanRHfix_Mg, REML = F)

coef(AAmRH_Mg)
summary(AAmRH_Mg)
anova(AAmRH_Mg)
plot(AAmRH_Mg)

AAtRH_Mg = sjPlot:: tab_model(AAmRH_Mg)
AAtRH_Mg

#create table with confidence intervals
resultAAmRH_Mg <- ggpredict(AAmRH_Mg, c("T","RHfix"))
resultAAmRH_Mg

Mg_AAp_RHfix <- interact_plot(AAmRH_Mg, pred = T, modx = RHfix,interval = TRUE,int.width = 0.95,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mg_AAp_RHfix <- Mg_AAp_RHfix + xlim(18, 25) +  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()



# Definir la ruta y el nombre del archivo
AAMg_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/AAMg_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = AAMg_RHfix, plot = Mg_AAp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")



#Detection Ranges
colnames(AADD_RHfix_Mg)
DDmeanRHfix_Mg <- AADD_RHfix_Mg[c(1:13,65,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(DDmeanRHfix_Mg)

#make interaction model
DDmRH_Mg <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Mg, REML = F)

coef(DDmRH_Mg)
summary(DDmRH_Mg)
plot(DDmRH_Mg)

DDtRH_Mg = sjPlot:: tab_model(DDmRH_Mg)
DDtRH_Mg


#create table with confidence intervals
resultDDmRH_Mg <- ggpredict(DDmRH_Mg, c("T","RHfix"))
resultDDmRH_Mg

Mg_DDp_RHfix <- interact_plot(DDmRH_Mg, pred = T, modx = RHfix,interval = TRUE,int.width = 0.6,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Mg_DDp_RHfix <- Mg_DDp_RHfix + xlim(18, 25)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDMg_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDMg_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDMg_RHfix, plot = Mg_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")

```

#Eptesicus brasiliensis 

```{r}

#Atmospheric Attenuation
colnames(AADD_RHfix_Eb)
AAmeanRHfix_Eb <- AADD_RHfix_Eb[c(1:13,60,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(AAmeanRHfix_Eb)

#make interaction model
AAmRH_Eb <- lmer(AAmeanFp ~ RHfix * T + (1|Ind), data = AAmeanRHfix_Eb, REML = F)

coef(AAmRH_Eb)
summary(AAmRH_Eb)
anova(AAmRH_Eb)
plot(AAmRH_Eb)

AAtRH_Eb = sjPlot:: tab_model(AAmRH_Eb)
AAtRH_Eb

#create table with confidence intervals
resultAAmRH_Eb <- ggpredict(AAmRH_Eb, c("T","RHfix"))
resultAAmRH_Eb

Eb_AAp_RHfix <- interact_plot(AAmRH_Eb, pred = T, modx = RHfix,interval = TRUE,int.width = 0.9,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Atmospheric Attenuation (dB/m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Eb_AAp_RHfix <- Eb_AAp_RHfix + xlim(18, 25) +  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))+
  scale_y_reverse()



# Definir la ruta y el nombre del archivo
AAEb_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/AAEb_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = AAEb_RHfix, plot = Eb_AAp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")



#Detection Ranges
colnames(AADD_RHfix_Eb)
DDmeanRHfix_Eb <- AADD_RHfix_Eb[c(1:13,65,63)] # column 59 is AAFp (atmospheric attenuation with observed values)

colnames(DDmeanRHfix_Eb)

#make interaction model
DDmRH_Eb <- lmer(avrgDD ~ RHfix * T + (1|Ind), data = DDmeanRHfix_Eb, REML = F)

coef(DDmRH_Eb)
summary(DDmRH_Eb)
plot(DDmRH_Eb)

DDtRH_Eb = sjPlot:: tab_model(DDmRH_Eb)
DDtRH_Eb


#create table with confidence intervals
resultDDmRH_Eb <- ggpredict(DDmRH_Eb, c("T","RHfix"))
resultDDmRH_Eb

Eb_DDp_RHfix <- interact_plot(DDmRH_Eb, pred = T, modx = RHfix,interval = TRUE,int.width = 0.6,
              vary.lty = FALSE,
              x.label = "Temperature (T°C)", 
              y.label = "Detection Distance (m)",
              legend.main = "RHfix",
              line.thickness = 2,
              colors = c("#394774","#78ccbf","#3a9eae"))+
              theme_apa(legend.font.size = 12,
              legend.use.title = TRUE,
              legend.pos = "none",
              x.font.size = 14,
              y.font.size = 14,
              remove.y.gridlines = FALSE,
              remove.x.gridlines = FALSE)

# Reversed y-axis
Eb_DDp_RHfix <- Eb_DDp_RHfix + xlim(18, 25) + ylim(1.1, 1.3)+ theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),
  plot.margin = margin(t=0.5,r=0.5,b=0.5,l=0.5,unit = "cm"))


# Definir la ruta y el nombre del archivo
DDEb_RHfix <- "F:/PhD_Project/Sensory_Ecology/R/R_figures/Reviewed/Def_plots/DDEb_RHfix.png"
# Guardar el gráfico en el archivo especificado
ggsave(filename = DDEb_RHfix, plot = Eb_DDp_RHfix, dpi = 300,width = 15, height = 10, units = "cm")

```
